"\textsc{Whew,} that was a real piece of work, I'll tell you!" Alfyn made a funny sort of whole-body gesture as he related the party's grand exploits in Noblecourt. Sunlight spilled over the table, and the beautiful girl with short-cropped golden hair seated across from him giggled as she listened to Alfyn's (somewhat embellished) story. So we set the scene: a tea party in the garden of the Ravus estate. How Alfyn came to participate will require a little explanation.

Alfyn was continuing to travel alongside his seven companions. They were a motley bunch with respect to origin, vocation, and motivations, but they got along well, and continued to support one another in working towards their respective goals. For one of those companions, Therion, the thief, the reason he had embarked on his journey was indeed that very House Ravus. In the course of their travels, the party made a stop in Bolderfall and decided it may not be a bad idea to say hello while they were there. And so, they had been invited to a tea party. As such, the girl now listening eagerly to Alfyn's tale was of course the current head of House Ravus, Cordelia Ravus. 

Alfyn, evidently quite charmed by his own storytelling, recounted to Cordelia one after another the events of one of the party's most recent exploits.

``And so, we walked way upstream -- turned out, there was a fella there poaching all the fish! No matter how much we talked to him, he jus' wouldn't listen, so Mr. Olberic and H'aanit...''

``Oh, my. So how did all it turn out?''

``Well, eventually all the fish came back to the river just fine, so it all wrapped up with a happy ending! Tressa wouldn't stop fumin' the whole time, though -- said she couldn't believe someone would hog all those fish to themselves like that, way more than anyone could eat.''

So far only Alfyn had been chatting up a storm, but of course he was not the only one there. A little behind Cordelia stood her butler, Heathcote, and Therion, naturally, occupied a seat as well. He hadn't spoken a single word since they arrived, and the tea prepared for him sat untouched on the table. Therion had been adamantly opposed to the idea of stopping by House Ravus in the first place, so perhaps that was only natural. Alfyn had had to drag the man half by force out of the inn. Primrose had joined them as well. \emph{So that you don't offend our noble hosts}, apparently.

``Would you care for another cup of tea, madam?''

``Yes, I'd love one.'' She smiled softly at Heathcote -- as always, she was unmatched in her grace and elegance. Alfyn was reminded once again how different her upbringing was from his own.

``I'm glad you're here to share all these interesting stories. Since Mr. Therion won't talk at all...''

``No kiddin'!'' Alfyn crossed his arms and nodded in firm agreement. Then, for the first time, Therion opened his mouth.

``It's only natural. I've got no need to talk to you. The only thing I agreed to do for you was steal back the three dragonstones. Am I wrong?''

``W-well, yes, but...'' Cordelia seemed to lose her words at Therion's accusatory tone. She hung her head.

``H-hey now, Therion, there's no need for all that, is there?''

``Once again. Am I wrong, medicine man?''

``I'm not sayin' you're wrong, just the way you're saying it is a bit rough, is all.''

``Hmph. Don't care.'' Therion had embarked on his journey to steal back House Ravus' three missing dragonstones. Of course, he wasn't doing it out of a sense of duty or out of the kindness of his heart. There was a reason there, one which implicated both his pride and his honor as a thief, but it wasn't something he'd frivolously allow an outsider like Alfyn anywhere near. At least, the few times Alfyn had tried to chat or crack a joke at Therion, he'd made no reference to it.

At any rate, Therion had pledged to use his skills as a thief to steal back the heirlooms of House Ravus. Alfyn had actually helped Therion out to steal one of the dragonstones from a scholar in Noblecourt. There was more than one place where the heavy labor made Alfyn want to groan out a complaint or two, but, just as promised, he saw with his own two eyes Therion's incredible skill as he deftly snatched away the red dragonstone.  Therion then returned to Bolderfall to deliver the stone to Heathcote and Cordelia directly. Alfyn hadn't accompanied him, of course, but he was pretty certain Therion didn't go in order to boast about his success at the work that had been foisted upon him. \emph{(Well, he ain't exactly the guy to brag about his accomplishments in the first place, is he...)} Alfyn thought, watching Therion's demeanor.

Primrose cut in before the atmosphere could sour any further. ``Oh, Alfyn, how about you tell her \emph{that} story next? It's quite the tale, after all.''

``\emph{That} story?''

``From before we arrived in Bolderfall. It was quite the struggle fighting off that herd of monsters, wasn't it?''

``Oh... Ohhhh, right, \emph{that} story! Yeah, alright!'' Alfyn once again clapped his hands and nodded with gusto.

It had happened only yesterday, a couple days after making their way into the Cliftlands. Bolderfall was right before there eyes when they were attacked by a flock of Birdians. Alfyn wouldn't go so far as to say it was `quite the struggle,' though. As she often did while the party made camp, Ophilia had split off to pray when she was set upon by the Birdians. The rest of the party had rushed to her aid immediately, though, and made short work of fending them off. Still, Primrose had a good idea -- if Alfyn could spice up the story a little bit to make it more of a thrilling tale, they could salvage the tea party's rapidly-sinking mood. Primrose really was handy to have around at times like this.

``...I think I'll take my leave now, then,'' Therion muttered, standing from his chair.

``Eh? O-oh, let me at least see you out, then, Mr. Therion...''

``Don't bother. We're here in the first place because our medicine man over here said we should come greet you all. We've greeted you all. So I don't have any reason to stick around, do I?''

``W-well...''

``I don't need you looking after my well-being. Either way, I'll take back the last two dragonstones.'' Therion's voice was as icy as ever. Cordelia made to follow him out anyway, but Heathcote stopped her. The gentleman's gaze, vigorous despite his age, met hers, and he shook his head softly. Cordelia clenched her fists and lowered her head. 

``I understand what Mr. Therion is saying, but... I mean, I'm the one who put the cuff on him in the first place...''

``I see. You made a pact with Therion that you'd remove the Fool's Bangle if he returned your heirlooms, is that right?'' Primrose nodded at Cordelia's words and set her teacup down. ``Then I imagine he has some rather complex feelings towards you. Please, try not to take too much offense at it.''

``No, it's not that I'm offended, I just...''

``...On top of that, I have a feeling that the reason he left is simply that the story Alfyn is about to tell might be rather embarrassing for him.''

``Eh...?'' Primrose chuckled a little; Cordelia's shock was written all over her face.

``You see, when Ophilia was attacked by monsters, the very first person to come to her aid was Therion, after all. Isn't that right, Alfyn?''

``H-Huh? Y'know, now that you mention it, you're right...'' At that time, Therion simply happened to be the closest to Ophilia's location, but the way Primrose said it made it sound as though he'd rushed to her side like a knight in shining armor. He was the closest, so he moved the fastest -- it really didn't go any further than that. Not only that, Ophilia was defenseless while she was praying -- Therion doubly needed to move quickly in order to cover her. Nevertheless, Alfyn spun the tale for Cordelia, embellishing here and there in order to make Therion look as good as possible. He wasn't quite certain how much of it she believed, but at the very least it seemed as though she was enjoying the story. That was enough for Alfyn.

\fancybreak*\pfbreakdisplay

When they finished their story, the sun had begun to set. In the Cliftlands, surrounded as it was by its sheer precipices, sunlight hours tended to be shorter. Night fell in Bolderfall faster than in neighboring regions. Bringing their conversation to an end, Alfyn and Primrose gave House Ravus their regards and departed from the estate.

``Still, it's a relief,'' Cordelia said as she saw them out. 

``A relief? What is?''

``To know that Mr. Therion has such kind traveling companions. Keep taking good care of him, alright?'' As Cordelia bowed profusely, Alfyn and Primrose's eyes met. \emph{Taking good care of him}, she had said.

Of course, Alfyn thought of Therion as his companion. But he was tight-lipped, unsociable, and often outright rude. One couldn't ever really know what he was thinking. \emph{He really ain't easy to get along with, huh?} was a thought that had crossed Alfyn's mind more than once or twice. Still, when he'd offered to buy Therion a pint back in Noblecourt, the man had willingly joined him for a drink. \emph{Can't be such a bad fella after all, eh?}, he'd thought at the time. Alfyn couldn't help himself from wanting to know more about him.

``Yeah, leave him t--'' ``Of course, leave him to us. Therion is our dear companion, after all.'' Alfyn and Primrose started to say the same thing at exactly the same time, but only Primrose finished her thought while Alfyn's mouth uselessly flapped open and shut for a moment. 

As they left the Ravus estate and made their way back to the inn, Alfyn and Primrose chatted a little.

``Cordelia's really a good egg, isn't she? Seems like she's worried an awful lot about Therion.''

``Indeed. Not only is she kind, I think she must also be an incredibly strong person.''

``Strong?'' It wasn't a word Alfyn easily associated with sweet, dainty Cordelia. Primrose nodded lightly.

``She's surely been through many a hardship until now...or so it seems to me, anyway.''

``'Many a hardship?' What d'you mean by that?''

``Who knows?'' Primrose turned to look back at the Ravus estate. ``I imagine outsiders like us couldn't even begin to guess.''

``Then what makes ya so sure about it in the first place?''

``Hmm... call it a woman's intuition?''

``G-gotcha...'' Alfyn had a feeling she was just trying to dodge the question, but maybe there was something to this `woman's intuition'... He decided to stop poking further and leave it at that. While Alfyn was mulling this over, Primrose, uncharacteristically, continued the conversation by changing the subject.

``Say, Alfyn? Have you ever noticed? Therion's bangle, I mean.''

``The... `Fool's Bangle,' was it? Seems to me like it'd be the ultimate humiliation for any thief. Figures that Therion's so desperate to get the thing off.'' Therion never wore anything but long sleeves, and he was always making great pains to conceal the bangle as much as he possibly could. Even Alfyn could figure out that much, which is why he'd made a point to never ask Therion about it. Primrose chuckled at the unusual grimness on Alfyn's face.

``No, not quite. You see...'' Just as they reached the inn entrance, Primrose leaned over and whispered in Alfyn's ear. As soon as he realized what he heard, Alfyn's eyes widened in shock.

``Haw!? You're kiddin'! I mean, Therion...''

``I'm not kidding, I promise you. I clearly saw it myself.''

``B-but then, why would he...?'' Primrose once again chuckled at Alfyn's astonishment.

``Who can say? But once I realized, I felt a lot better about having him as our companion, honestly. It clearly shows that Therion isn't the type of thief to work for nothing but his own gain, don't you think?'' Primrose opened the door to the inn and walked inside. ``Well, goodnight, Alfyn.''

``Y-you, too...'' As he watched Primrose go, Alfyn folded his arms and replayed her words in his mind. ``So all this time, Therion's been...'' He already had the inkling of the idea that Therion wasn't so bad after all, but he still couldn't quite believe what Primrose had told him. ``I wonder where he scurried off to. Sure doesn't seem like he's back at the inn yet... Maybe I'll walk around a little and look for him.''

\fancybreak*\pfbreakdisplay

Not long after he set out, Alfyn ran into Olberic and the others on their way back from their errands. When Tressa heard they'd gone to greet House Ravus, she mournfully rued missing a valuable business opportunity by choosing to accompany Olberic. The full story would take a while, though, so they decided to leave it at that.

The town of Bolderfall was cleanly stratified into three sections, the lowest of which consisted of a rowdy slum. Bolderfall already suffered from a dearth of taverns, but the vast majority of those alehouses that were there were concentrated in the slums. If Therion was still out and about, Alfyn figured he might find him there.

Even though geographically, the Cliftlands were relatively close to Alfyn's native Riverlands, the two couldn't have seemed further apart. Bolderfall's townscape, too, was utterly foreign compared to Clearbrook's pastoral scenery. 

It had been a shot in the dark in the first place, but Therion was still nowhere to be found. After walking around the slum for a while, Alfyn decided to rest for a moment and plunked himself down on a flight of stone stairs.

``Oh, 'scuse me, little miss!'' As cheerily as ever, he offered a greeting to a small girl similarly seated on the stairs. Her head shot up, apparently surprised at having someone unexpectedly call out to her. It was then that Alfyn noticed she had still-fresh scrapes on her cheek and knees. Maybe she'd fallen down those stairs?

``Woah, you're hurt! Let me take a look.''

``H-Huh? B-but...''

``Don't you worry! Even if I don't quite look it, I'm actually an apothecary!'' He produced a pre-prepared salve from his medicine bag and moved to apply it to her wounds. Before he could, though, the girl squeaked out,

``U-um, I don't have any money...''

``That's alright, I'm not askin' for your money! It's not good to try n' just grin and bear it with scrapes like these.'' Finally, the girl nodded slightly. Once Alfyn finished examining her injuries and applying the salve, he said gently, ``Now, it's gettin' awful dark. Stay safe heading home, okay?''

``O-okay...'' The girl briefly bowed, then disappeared once again into the crowd. As he watched her go, he put his hands on his hips and gave a satisfied nod.

``And just what are you up to, medicine man?''

``Gyah!!'' Alfyn jumped at the sound of a voice from behind him. He whirled around to find a man a little shorter than him, with a nasty expression on his face, glaring at him with suspicion.

``Th-Therion!? Guess you've saved me some time lookin' for you, but don't go scarin' me like that...''

```Lookin'' for me? Why? There's still time before we're supposed to leave, isn't there? If you wanted me to stay in one place so badly, you should've put a rope around my neck.''

``Y-You're not a horse, y'know...'' Alfyn strained a smile at Therion's incorrigible bluntness. He moved to the side of the street to avoid the throng in the center, and Therion followed. He stole a glance at Alfyn's medicine bag and sighed.

``I saw that, you know. You keep showing off your strange brand of kindness in a place like this, someone's gonna pull the rug out from under your feet before long.''

``What's that `strange brand of kindness' supposed to mean? I just wanted to make sure that little girl got her scrape looked at...''

``And that's exactly what I mean, medicine man. What if, hypothetically, that girl was some pickpockets' accomplice? What would you do then, huh? As soon as you go to pull out your medicine, they could swipe anything of value off you in an instant.''

``Eh!?'' Panicked, Alfyn quickly went to check his bag, only to find that -- thankfully -- not a single leaf was out of place. To be certain, he rifled through his other belongings and confirmed that nothing else was missing. ``Nothin' to worry about. She didn't steal a thing!''

``I said \emph{hypothetically}, didn't I? All I'm saying is there's nasty characters out there, ready to take advantage of your generosity by wheedling medicine out of you.''

``I guess, when ya put it like that...'' Alfyn scratched his head. Therion clicked his tongue.

``Now, don't follow me.''

``C'mon, you don't gotta be so upset...''

\fancybreak*\pfbreakdisplay

Alfyn followed behind Therion, matching the thief's brisk, determined pace. His pace was fast, but Therion simply walked with a huff, without telling Alfyn to get lost or go away, until the two walked through the front door of a tavern in the middle of the slums. Alfyn sat himself at the same table as Therion. The other man let out a sharp sigh.

``I thought I said \emph{not} to follow me.''

``Didn't I say I was lookin' for you? I was in the mood to grab a drink with you.''

``We've drank together once already, haven't we?''

``And how long ago was that, huh? That was then, and this is now!'' After all, the whole reason Alfyn had been searching for Therion was to get the chance to speak to the man. Primrose's words from earlier still played in his mind, and he kept shooting furtive glances in Therion's direction to try and confirm them for himself, but he continued to hide his wrist with the most natural-seeming of gestures. Perhaps he'd noticed Alfyn staring.

``Got a problem?''

``N-naw, not at all...?'' The ale they'd ordered arrived and Alfyn made to raise his glass, but Therion refused to follow his lead, merely lifting his own tankard to his lips.

\emph{Damn, he} really \emph{ain't easy to get along with,} he thought once again. He tried to think of something he could try and use to make conversation, settling on talking about his own past.

``S-say, did I ever tell you? 'Bout how I've got a good pal back home, an apothecary just like me.''

``...'' Therion continued to sip his ale, all the while glaring at Alfyn. His fierce gaze from behind his white hair seemed almost to stab Alfyn, and he felt cold sweat drip down his neck as he nevertheless continued talking.

``His name's Zeph. Maybe if we end up swingin' round Clearbook one of these days, I'll introduce you. He's a real good guy. We've been runnin' around together ever since we were kids, so he's honestly like somethin' closer to a brother to me.''

``A brother, huh...'' Therion muttered, barely more than a whisper. Alfyn was honestly delighted to have elicited a response at all from ever-brusque Therion.

``Yeah, a brother! I can't say I thought of him like that till right now, but it sure fits. When I told him I was settin' out, he was nothing but supportive -- to be honest, Zeph gave me the last push I needed to hit the road. If it weren't for him, I don't think I'd be traveling with y'all at all.'' \emph{I was just talkin' in the heat of the moment}, Alfyn thought, \emph{but I sure can't deny there's truth to that.} Alfyn had begun his journey in order to help people all over the world with his medicine. That way, he thought, he could save others' lives just like the man who had once saved his own. But by giving him the courage to depart, not only had Zeph helped Alfyn start to fulfill that dream, he had given him the opportunity to meet Therion and their other companions. He couldn't help but think of that as a precious treasure.

``I see. That Zeph certainly seems like a good friend of yours.'' Therion nodded, setting his now-empty tankard back on the table.

``Y'see? Glad you think so, too--''

Therion cut him off. ``But at the end of the day, no matter how good a friend he is, you're still unrelated. Just another person,'' he said curtly. Alfyn was at a loss for words, crushed by his misunderstanding of Therion's agreement, as Therion launched a follow-up attack. ``You can yap about your `brother' all you want, but you really are more naïve than I thought, medicine man. When all's said and done, you're just yourself. Other people are other people.''

``Y-ya think...?''

``I do. Then that makes us two nothing but perfect strangers.'' Therion crossed his arms. Total rejection brimmed from his eyes, boring into Alfyn. \emph{We're not ``companions.'' There's no way we can ever really understand each other. So don't go prying any further.} He may not have said as much in words, but his aura more than insinuated it. Even Alfyn couldn't stay on the offensive when confronted head-on with such an attitude. 

``You show too much of that kindness, that gentleness, to others, the only one who's going to pay the price for it is you.''

\emph{So don't show them any weakness they can take advantage of.}

\emph{Just live only for yourself, and that can be the end of it.}

Therion tossed the leaves for his ale on the table and stood up. Without saying another word to the speechless Alfyn, he turned his back to him and left the tavern.

``...'' Alfyn could do nothing but watch him go. No matter how optimistic he always managed to be, even he couldn't hide his shock. ``What in the world happened to him...?'' Is that really how he feels, from the bottom of his heart? \emph{You're just yourself. Other people are other people. So you shouldn't bother associating any further.} Could someone who thinks like that really exist?

``Then Therion, why go and...?''

``Oi, brother! What's got you all down in the dumps now?'' Alfyn's muttering was loudly interrupted by a wildly overeager shout. Alfyn looked up, surprised, to find a pair of men he'd never met at his table, clapping him on the shoulder. Their faces were rough, and their voices sounded slick with alcohol -- the kind of people one could find in any town's slums. Alfyn forced a strained smile onto his face. 

``Ahh, my bad. Just had a nasty sip of my drink here -- guess it showed on my face.''

``Somethin' bad happen to ya? Eh?'' ``Come on, we'll hear you out, yeah?''

After getting lectured like that by Therion, Alfyn was honestly glad to hear some kind words from these men he'd never met. Alfyn's bitter smile morphed into his genuine trademark grin. He quaffed the rest of his ale and set the tankard aside.

``You sure know how to drink, brother!'' ``Nothin' bad you can't forget with some drink!'' Grins split across the men's faces as they clapped Alfyn's back again -- and again, when they saw Alfyn's own smile.

``Got that right, friend! Guess you could say this is some kinda fate -- have a drink with me!'' \emph{Maybe Therion's right -- maybe other people really can't be more than strangers. But so what? The world's full of all kinds of folks.} Alfyn ordered another round.

\fancybreak*\pfbreakdisplay

\emph{He's honestly like somethin' closer to a brother to me.} Buffeted by the night wind, Therion turned Alfyn's words over in his mind. The gusts blown up from the valley floor, characteristic of the Cliftlands, tousled Therion's snow-white hair. Refreshing as the night wind was, it didn't blow away the lingering aftertaste of cheap liquor, nor did it help to quell the whirlpool of emotions brewing in his chest.

To Therion, the word ``brother'' held a special meaning -- especially when used to refer to a connection not of blood, but of particular familiarity.

\begin{center}
    \emph{Therion, huh? That's a good name. Nice to meetcha, brother}\endnote{The English localization of \emph{Octopath Traveler} has Darius and Therion use the word `partner' to refer to one another. The original Japanese word is \emph{kyoudai}, which literally means `brother(s)' or `siblings,' but can also mean something similar to `partner in crime,' as it is also used to refer to sworn brothers in, e.g., organized crime. These lines are verbatim from the game in Japanese, but since they either use the word `partner' in place of \emph{kyoudai} or omit it entirely in the localization, I had to rewrite them to include `brother,' as this conflict relies on the intermingling of the various senses of the word.}\emph{!}
    
    \emph{Damn... I'm no match for you, brother!}
    
    \emph{Why? Simple, brother.}
    
    \emph{Now, die for me. ...Brother.}
\end{center}
``...Darius.'' The words spoken by the man Therion had once called his brother replayed in his mind. He was the first person Therion, as a lonely young man, had ever learned to trust, and the first person to ever betray him. Then, too, the wind was howling up from the valley as Darius' assault sent Therion plummeting to the bottom of the cliff.

Darius had done nothing but use Therion. He had discovered Therion's genius as a thief and used it as a stepping stone for his own gain. Certainly that was nothing like Alfyn's relationship with Zeph. Certainly theirs was built on a relationship of mutual trust, without self-serving calculation -- one look at trusting, naïve Alfyn and he could tell. And certainly as Alfyn thought of Zeph as his brother, Zeph would think of Alfyn the same.

Then what about Therion himself and Alfyn? Not just Alfyn -- what exactly was his relationship with the seven others he was traveling with? Therion had chosen to continue traveling by their side because it was convenient, and nothing more. When it came to a fight, a warrior and a hunter were valuable to have; when there was information to be gathered, it was a scholar's time to shine; and when deploying even Therion's pickpocketing finesse proved troublesome, letting a merchant handle the business negotiations made obtaining valuables painless. 

Indeed, Therion was doing nothing but taking advantage of them -- just as Darius had done to him. Yet it was precisely for that reason that he wanted to avoid showing the others any sign of weakness.

``...'' As he walked, Therion felt a disturbance in his usual sense of balance; a chill down his spine and a strange bodily sensation. He realized these were the signs of some kind of illness. Fortunately, he knew a few empty houses nearby from the years he was active in the area. He could lay low in one of them and, hopefully, recover in time to regroup with the others before they left Bolderfall.

As he passed through the slums, a vulgar, thick voice grated on his ears, interrupting his thoughts. 

``Nice goin', brother!''

``A rube like him? That weren't nothin'!'' 

Therion turned around to see two of Bolderfall's dime-a-dozen ne'er-do-well thieves strolling along in high spirits. \emph{Pulled off a good job, huh? That's nothing to sneer at}, Therion thought, but as he watched the two pass, he narrowed his eyes at their hands. They were, without a doubt, holding Alfyn's belongings. One of the thieves opened his wallet and peered inside.

``Seems he wasn't carryin' any leaves on him.''

``Damn, ain't apothecaries supposed to rake it in? Didn't expect that. Can probably make good coin off these, though.'' \emph{Tsk}. ``These'' meant Alfyn's apothecary tools. Therion didn't have a clue how any of them were used, but he could at least tell that Alfyn took carrying them around seriously. \emph{Just as I thought. Looks like someone took advantage of him after all. Can't say I didn't warn you. If those tools were so important, why would you put them somewhere where anyone could lift them off you?}

``He's probably worryin' about how he can't even pay for his ale right now! Poor guy!''

``His fault for sittin' there with a face practically screaming, `I'm an easy mark, come rob me,' ain't it?'' 

``Got that right! Gyahaha!'' Oblivious to Therion's gaze, they put Alfyn's wallet and tools back in their bag and began walking off again towards another pub -- no doubt to buy themselves another round with their spoils. He watched them go in and staggered along once more.

\fancybreak*\pfbreakdisplay

``You got some nerve, thinkin' you can get yerself a free drink off me, boy!''

``N-no, I wasn't-- It was just there, I swear! It can't be...'' The barkeep stared down Alfyn with a menacing glare as he frantically scavenged for his missing wallet. Just moments ago, he'd decided to leave the tavern, only to find when he went to pay that his belongings were nowhere to be found. Of course, checking the pocket he usually kept his wallet in and turning his coat inside-out did him no good. Then, what about his bag? Just as he went to look inside, he was interrupted by a familiar voice from behind.

``And just what are you doing, medicine man?'' Alfyn whirled around, surprised.

``Th-Therion$\sim$!'' The small-framed thief was staring at him, arms crossed. Alfyn broke into a wide grin as he called his name. Therion looked back and fort from Alfyn's pathetic smile to the barkeep, veins bulging out of his head, and instantly surmised the situation.

``Barkeep, I'll cover for him.'' Alfyn had clearly been relieved just at Therion's mere arrival, but it didn't seem he expected Therion to actually come to the rescue. After all, it was Therion who had just admonished him so mercilessly.

``Eh? Therion, you sure?''

``I didn't say I'd be \emph{treating} you, medicine man. You'll pay me back.''

``N-naw, I got that, I just... Thanks. You're a big help.'' Shaking off his bewilderment, the first things that came out of Alfyn's mouth were words of gratitude. At any rate, Therion had rescued him from this particular pinch. His thanks were accompanied by a friendly smile. Without responding in kind, Therion merely walked to the tavern door. Just as he was about to leave, though, he asked Alfyn,

``Where's your wallet?'' Alfyn gave a bitter smile and rubbed the back of his neck, embarrassed, as he answered,

``Guess I lost it.'' The instant he said that, he felt a trace of danger enter Therion's gaze. Therion so rarely let people read his expressions, but Alfyn could clearly detect a quiet anger emanating from him. He didn't realize it, but the target of his ire was Alfyn himself.

``It was \emph{stolen}.'' His voice was low and his reply brief, but his announcement was more than clear.

``A-ah... That so?''

``It was \emph{stolen} because you're so \emph{obviously} soft, and it makes you defenseless. In the time it takes to cross this room, I could strip you naked and rob you blind.''

``Sorry, but if it comes to that, think ya could at least let me keep my underwear?''

``...'' Alfyn's joking reply, rather than lightening the mood, instead only served to get on Therion's nerves. ``You are aware I'm a thief, aren't you? What guarantee do you have I wouldn't do that?'' He closed in on Alfyn and lifted him by the collar.

``W-what are you sayin'? Therion, there's no way you'd do somethin' like that, right...?'' Good-humored Alfyn, with understanding of why his traveling companion -- even if he was a thief -- was targeting him with such naked rage, wasn't sure at first whether he should apologize or fight back.

It was then that he noticed that Therion's thin body seemed to be staggering. No -- it didn't merely look that way; his balance was shaky, and the trunk of his body was unsteady. At the same moment, he noticed for the first time the drops of sweat beading on Therion's face. 

``Woah there, Therion, you're not well, are you?'' He was careless for not noticing until now. No, that wasn't right. Therion had made sure he wouldn't notice. Not because he didn't want Alfyn to worry, but rather out of a refusal to show any sign of weakness to anyone else. ``What happened to you? Let me take a look.''

``Don't... Don't worry about it...!'' Therion slapped Alfyn's hand away. He still had more strength than Alfyn expected. As if nothing was wrong, Therion walked a little further, leaving the tavern, but before long crumpled again, clutching the fence overlooking the cliff face.

``Hey, look out!'' Alfyn made to support him, and this time, Therion had no strength left to shake off Alfyn's hands. He was running a high fever. It was obvious he had been overdoing it for far too long, and that the symptoms had suddenly taken a turn for the worse over the course of just a few hours. Alfyn lifted the languid Therion onto his back, slung his now-empty medicine bag over his shoulder, and sprinted for the inn.

\fancybreak*\pfbreakdisplay

``He's got peacock fever.'' Alfyn closed the door of the room where Therion had been put to bed and announced his diagnosis. The inn corridor was packed with their companions, staring at him with variously concerned expressions. ``It's carried by avian monsters and spreads through open wounds, but it's nothin' too tough to treat. I know how to make the medicine for it, too; 's just a matter of gettin' ahold of the ingredients.'' 

``What do you need?'' Olberic asked. Naturally, he immediately understood what Alfyn was trying to say. Of course, it wasn't just him; the rest of the party nodded at Olberic's question. Alfyn glanced at the door behind him as he responded,

``Peacock fever's carried by avians, but they don't get it themselves thanks to their natural resistance to it. So all I need is the blood an' feathers of an avian -- the bigger the better. Then I can whip somethin' up with the ingredients I keep on hand. It's just a question of whether we'll be able to find one big enough...''

``Aha...'' Cyrus realized something and raised his head. ``If I remember correctly, I believe there are several caves in the Cliftland valley which were once used for sky burials -- the bodies of the deceased would be left there to be eaten by birds. I'm certain we ought to find a monster that suits your needs there.''

``Very well, then we shall look there.'' They came to a conclusion at once. The sun was already setting, and there was no small danger in traveling the mountain roads of the Cliftlands under cover of darkness, but no one raised any objections at setting out then and there. Without any thoughtless remark on the risk his companions were taking on, Alfyn merely said,

``I'm countin' on you, sir.''

``Of course.'' Olberic and the others made their preparations and set out to gather Alfyn's ingredients at once, leaving their various parting words: Primrose's \emph{We'll leave the bedside care to you, then}; H'aanit's \emph{We willen return anon -- waite but a moment}; and Tressa's \emph{Tell Mr. Therion I hope he feels better!} Alfyn and Ophilia were the only two who remained to look after Therion. While they waited for the materials, all they could do was continue treating his symptoms, laying an cloth wet with ice-cold water on his forehead and disinfecting and wrapping his wounds. Fortunately, the party had just restocked, so there was no shortage of supplies.

``Mr. Alfyn?'' Ophilia suddenly whispered while carefully continuing her treatment. ``If Therion has peacock fever, then he must have caught it when...''

``Yeah, must've been, huh...'' Their close encounter with a flock of Birdians had occurred only a couple days before arriving in Bolderfall. Therion was the one who had rushed right to Ophilia's side as they attacked her. When Alfyn and the others caught up to him, it didn't seem as though he was hurt, which was surely why he had been too late to notice Therion's symptoms, but he had indeed sustained a fierce gash on part of his arm covering Ophilia from the Birdians' assault. 

``It's nothin' you ought to fret over, Ophilia.''

``...Of course.'' It seemed Alfyn thought she was blaming herself. ``After all, just as Mr. Therion saved me then, I'm returning the favor and save him now.''

``Now, ain't that a good thought? Well, then.'' Alfyn was honestly grateful to have Ophilia with him. She seemed to have experience nursing patients, and she was quick on the uptake. While they waited for the others' return from the valley with his ingredients, they split the job of taking care of Therion. The man himself was sleeping on the bed wearing a pained expression. It wouldn't be an exaggeration to say that no matter how unfavorable a position he found himself in, he would never let his anguish or despair show on his face. The thief was so steadfastly dedicated to concealing any sign of weakness from others that it had taken him to the point of near-total collapse hiding his infection with peacock fever.

\emph{You're defenseless}. It had only been one or two hours ago that Therion, pressing up to him, had said that. The reason he hid his every weakness was to avoid ever being taken advantage of. He had lived alone that way his entire life -- he was probably alone even now.

\emph{You are aware I'm a thief, aren't you? What guarantee do you have I wouldn't do that?} Alfyn stared at Therion's face, drenched in sweat, and placed a hand to his own forehead.

``A guarantee, huh... Do I really need somethin' like that...?'' His voice wrung-out, the words slipped out of their own accord. \emph{Can't I trust you won't do that to me even without a guarantee? Is that really so wrong?} Of course, Alfyn trusted in Therion even now. It didn't matter that his wallet was stolen -- he was certain Therion wasn't the culprit. It was then he remembered Primrose's words to him earlier.

\emph{No, not quite. You see...} Just after they had left the Ravus estate, Primrose had whispered into his ear. \emph{...the lock on Therion's so-called ``Fool's Bangle'' has already been undone.} When Alfyn went to examine the wounds the Birdians had left on him, he looked at both of his arms. The bangle was certainly there, but when he put his hand to the clasp, it opened effortlessly with a tiny \emph{click}. The thief was already as free as he had ever been. There was no way Therion himself was unaware of this. He had already lost the very reason for reclaiming the stolen treasures of the Ravus family. Yet even now, he was dutifully covering his wrists with his long sleeves, continuing his journey with Alfyn and the others, and pursuing the same goal he had from the start.

``I guess, after all, you really do...''

``Mr. Alfyn?'' Ophilia tilted her head curiously and peered into Alfyn's expression. Only then did he realize he had been voicing his thoughts aloud the whole time. Even if he hurried to cover his mouth with his hands, it was too late. Embarrassment washed over him. ``If you're tired, perhaps it wouldn't be a bad idea to rest a little. You still have to make the medicine once everyone returns, after all--''

``N-naw, don't you worry! It's not that, I swear!'' As Alfyn waved his hands, desperately trying to defend himself, Ophilia giggled. 

``Were you thinking about Mr. Therion, I wonder?''

``W-well, I guess you could say that. Somethin' or another happened with him, y'know...'' Caught, Alfyn had no choice but to grin sheepishly. That's right, ``somethin' or another'' -- nothing there was any need to fight about. Therion had told him he couldn't put his trust in other people. Of course, that had seemed like nothing so much as an indication that Therion himself didn't put his trust in Alfyn. Yet that couldn't explain Therion risking his life to protect Ophilia, nor could it explain continuing his journey to restore the Ravus treasures to their rightful owners. Alfyn couldn't pretend he understood everything about Therion, but he felt that a piece of the other man's true feelings revealed itself in that tiny contradiction. ``Therion told me, `You're just yourself. Other people are other people.' -- that I'm a right fool for trustin' him or anyone else,'' Alfyn continued, recalling the words Therion had spat at him. ``But if you look at it that way, then no matter how far we travel, that means that I'm still me, and Therion's still Therion, right?''

``I suppose so. You're Mr. Alfyn and no one else, of course.'' Alfyn's manner of speaking lacked certainty, but Ophilia thought she understood what he was trying to say. 

Therion had a sharp tongue and spoke bluntly, and there was no denying he could be endlessly difficult to get along with, but as far as Alfyn was concerned, he wasn't a bad person at all. On the contrary -- though the man himself would probably laugh in his face if he said so -- Alfyn thought of him as, in his words, ``a real good guy.'' No matter what Therion said or what attitude he took, that was just the kind of person Therion was. In the same way, worrying after Therion and working to cure his illness, even when Therion would never ask him to, was just the kind of person Alfyn Greengrass was.

``Alright! I'd better get things set so I'm ready to go whenever Sir Olberic 'n the others get back!'' Hyping himself up, Alfyn opened his medicine bag and went to pull out his synthesizing equipment and medicinal herbs. He stared into the bag and instantly paled.

``What the--?!''

``Wh-what's the matter?''

``They're... gone...'' His tools were gone. Missing. Simply not there. That was impossible -- he had put a salve on that little girl who fell on the steps just that evening. He was certain they were in his bag then, and he hadn't opened it since, so it was difficult to imagine they'd simply fallen out. If they'd been stolen, then he had no choice to admit Therion had been right about that. It was his fault for realizing only now, but it occurred to him that perhaps the thief hadn't been simply conjecturing.

At the tavern -- that pair of men.

``Th-those bastards...!'' The normally easy-going, mild-mannered young man had a look of utter betrayal on his face. He should have realized how light his bag was when he was carrying Therion. Perhaps he had simply been in too much of a hurry.

``M-Mr. Alfyn...?''

``Ophilia, can you look after Therion!? I gotta head out real quick!'' Alfyn opened the door and flew out of the room almost before he'd finished his sentence. He had no clue where the two thieves could be, but he didn't have any choice but to get searching. At a time like this, Alfyn was the kind of person whose body moved before he had a chance to even think.

``M-Mr. Alfyn--!'' Alfyn dashed away from the voice calling out to him and into the night of Bolderfall.

\fancybreak*\pfbreakdisplay

\printendnotes
% page 91

% TODO:
% workshop primrose voice ;-;
% "widened in shock" mmmm reword maybe
% "自分は自分、他人は他人" tl
% add fancybreaks