\textsc{``I cannot} agree to this, H'aanit. It's too dangerous.'' Olberic's face was grim -- but that was only natural. The party was in the town of Stillsnow, which, just as the name suggested, was blanketed year-round in a layer of silver-glittering snow. However, the blizzard raging outside was unusual in its ferocity even for the Frostlands. The windows of the lodge, which should have been more than sturdy enough to withstand a snowstorm, rattled perilously, and the view outside, even though it was nighttime, was pure white as far as the eye could see. Yet amidst the fierce snow, H'aanit was determined to search for Ophilia.

``I knowe 'twill be dangerous -- but I do not intende to doen anything rash, nor am I without preparation.'' H'aanit's voice was strained but firm. Hers certainly was not the voice of someone who had lost their cool.

``But...''

``'Tis no trouble for me to followen Linde's tracks, even if they be faint, and the place is not so far from here.''

It was a few hours ago that the party had been separated from Ophilia. Snow began to fall as they left the white forest behind and were making their way back to Stillsnow, and although the distance wasn't particularly far, their vision was stolen in an instant. Disoriented by the harsh snowfall, Ophilia took a wrong step, lost her balance, and slipped away from the rest of the group.

Ordinarily, it would be a given for ever-attentive Ophilia to proceed with caution and certainty, even in such harsh conditions. Yet for the past several days, she had been clearly wracked by some kind of worry, and it had begun to tinge her behavior with a certain lifelessness -- ultimately culminating in her slip and fall. H'aanit had rushed over in an instant and stretched out her hand, but couldn't get ahold of Ophilia's arm. With a blank expression on her face, as though she herself wasn't quite sure what was happening, Ophilia disappeared into the snow in the blink of an eye.

As her companions rushed to find a way to rescue her, the one who acted with the greatest clarity of purpose was none other than the snow leopard Linde. H'aanit exchanged a brief glance with her companion and understood what Linde meant to do at once. Some food, alcohol, and the other bare necessities to endure the bitter cold were strapped to Linde's body before she, too, disappeared into the snow, determined to follow after Ophilia.

Unfortunately, as long as the party was unable to properly get their own equipment and supplies in order, it was too dangerous to remain in the middle of the blizzard any longer. There was nothing else for them to do but make the trek back to Stillsnow.

``Linde haileth from the Frostlands,'' H'aanit said as she donned her pelts and laced snowshoes to her boots. ``Even amidst a blizzard such as this, 'twould be a trifle to finden her quarry. I've no doubt she is fast at Ophilia's side by now -- but whether she is unharmed is a separate question, indeed.'' H'aanit cast her gaze towards the snowstorm on the other side of the window. ``In conditions such as these, the danger that she maye freeze to death only groweth, and Linde's tracks willen growe harder to finden. If we are to searchen after her...''

Cyrus, who had remained silent until now, interjected, ``I see. The time to follow after her is now, while we can still hope for both her safety and finding Linde's tracks,''

``...Just so.'' H'aanit nodded. Olberic's expression remained severe, and he let out a groan.

``Still, it's dangerous for you to travel alone. Perhaps it would be better to have someone else accompany you...''

``I'm not so sure of that, Olberic.'' Cyrus laced his fingers together before the fireplace. ``Someone like H'aanit, a hunter from S'warkii, might be accustomed to navigating the middle of a blizzard like this, but I don't know if we can say the same of anyone else. I'm sure a knight of Hornburg has some experience traveling through snow, but I doubt you've had to weather a snowstorm like this, am I right?''

``...It's as you say.'' Olberic sighed. H'aanit imagined that was precisely the cause for his concern -- Olberic was the only member of their party with experience commanding troops, and that made him all the more inclined to take up the role of opposing any rash movements as a matter of principle.  On the other hand, it was as Cyrus said. H'aanit was more than accustomed to pursuing a target through even the worst conditions; she hadn't imagined the day would come where being forced to handle all her master's countless unreasonable requests would come in handy like this. She hardly wanted to suggest that bringing anyone else would just get in her way, but there was no denying that for something so time-sensitive, she would prefer to be able to move as lightly as possible.

As the party continued to mull over the best course of action, the door opened with a \emph{bang}, and snow-bearing wind entered the lodge room along with Primrose, shivering even while bundled up in her coat. As she dusted the snow from her hair with a grim look on her face.

``We had a chat with the people at Arianna's brothel -- they said once the storm calms a little more, they could arrange a carriage for us.''

``But at this rate, it's hard to say when exactly that'll be,'' Therion added, entering a little after Primrose, as he shut the door behind him. H'aanit thought over their predicament once more and finally said,

``There's no need for worry, Olberic. 'Tis heartening to knowen your concern, but I am not one to acten rashly -- rather, I am all too often one to advisen others against doing so. Should I determine it too perilous to proceeden, I shall returne at once.''

``...Very well.'' Olberic finally nodded, defeated. ``But please don't do anything risky, H'aanit. You know the saying -- the tiger bites he who chases after rabbits.'' 

``Thou wouldst really level such a proverb at a hunter of S'warkii?''

Ceding the fireside to Primrose and Therion, Cyrus chuckled. ``Speaking of proverbs, Olberic, perhaps `teaching Bifelgan his own trade' would be more appropriate?'' Olberic could really do nothing in response to that but let out a long sigh and shake his head, conceding at last, before allowing the corners of his mouth to slacken into a small smile.

``Quite right. Godspeed, H'aanit -- we'll leave Ophilia to you.''

At last fully dressed to keep the cold at bay, H'aanit, voice muffled by the pelt covering her mouth, replied, ``Of course.''

``H'aanit!'' ``Miss H'aanit!'' Before H'aanit could walk out the door, she was stopped by Alfyn and Tressa calling from behind. ``Ya never know what could happen out there -- lemme give you some salve for frostbite, okay?''

``And here's a hearthstone! If you get too cold, you can use it like a hot water bottle!''

``My thanks to you both.'' H'aanit nodded and accepted their parting gifts before opening the door and stepping outside. Throwing herself into the middle of the snowstorm, awaited by her companion and her partner, she, too, melted into the silver-tinted landscape before long.

\fancybreak*\pfbreakdisplay

When Ophilia Clement awoke, she found herself lying upon the rugged surface of a rock face. She reflexively shrank into herself, her coat (or any coat, for that matter) insufficient to keep the bitter cold at bay. Her consciousness still hazy, she surveyed her surroundings to realize she was in the middle of a cave.

``That's right... on the way back to Stillsnow, I...'' A full, throbbing pain began to spread throughout her body like a bruise. Pressing a hand to her forehead, she struggled to recall clearly what had happened to her. ``I, fell...? Right, I missed my footing...'' Ophilia cursed her own carelessness -- they had been traveling along a snowy road, and in the middle of a blizzard to boot. Even if she'd been restless, even if she'd been distracted, she should have known better than anyone among her companions how dangerous moving through such a snowstorm could be.

But it was no time for her to be throwing herself a pity party. Her worries were far from cleared, but what she needed to focus on now was making it back to the party alive. Odds were they were already back in Stillsnow and more than likely worried about her. She'd like nothing more than to return at once, but it would be foolish to try and blindly rush back into the middle of the blizzard. 

What Ophilia needed to do now was to get her bearings and get a clearer picture of her situation. With her vision obscured by the snow, she'd probably slipped and fallen to the side of the main road from a decent height -- luckily, without sustaining any serious injuries.

Inwardly expressing her gratitude to the Sacred Flame for shielding her from peril, Ophilia looked around her once more. There was one more person besides the Flamebringer deserving of her thanks:

``Just who carried me here, I wonder...?'' She'd fallen into the snow, which is what had let her escape with only bruising. If she'd been left there for much longer, though, her body temperature wouldn't have been able to hold; the fact that she now found herself in this cave was the only reason she'd avoided hypothermia or frostbite. As Ophilia cast her gaze around in search of her savior, it landed upon a large, shifting shadow -- a decidedly inhuman shadow. A nervous chill shot down her spine. Her adoptive father had often told her stories of the monstrous snow leopards found in the Frostlands. They were said to live in great numbers along the trail to the Whitewood, and Josef's fairy tales about them had always terrified the young Ophilia.

Luckily, she spotted her staff not too far away. Stiffening her face and putting on a dignified brave face, she managed to retrieve it. Trying not provoke the beast into lunging at her in an instant, she slowly backed away from the shadow in an attempt to maintain some distance.

``\emph{Grrr...}''

``...!'' That was unmistakably the low growl of a monster. Ophilia's eyes reflexively widened at the figure of the pure white beast now emerging from the shadows. ``Y-you're...!''

``\emph{Grrrrrr...}''

``L-Linde...!? Linde, is that you...!?'' She couldn't contain her disbelief at this sudden, unexpected appearance. Linde -- the snow leopard H'aanit kept at her side as her partner. She resembled the monstrous variety of snow leopard, to be sure, but small differences could be found in things like the shape of her ears. Most telling was the small leather bag wrapped around the neck of the beast before her; the bag, inscribed with the mark H'aanit placed upon all of her possessions, eliminated all doubt that this was indeed Linde. `` Linde!!'' Overjoyed at her reunion with one of her companions, Ophilia rushed to Linde's side and threw her arms around her neck. The warmth of her body heat could be felt through her soft fur, flooding Ophilia with relief. ``Oh, thank you! You saved me...!''

``\emph{Ghuu...}'' Linde purred softly. Ophilia wasn't exactly fluent in Snow Leopard, but she could tell at least that it wasn't a noise of displeasure. She then untied the leather bag fastened to Linde's neck and checked its contents. Inside she found a small amount of food and alcohol, tools for starting a fire, et cetera.

``Then H'aanit must have packed this for me...''

``...'' Linde seemed to surmise what she meant upon hearing H'aanit's name. She made a gesture something akin to a nod. \emph{What a clever girl}, Ophilia thought. She'd never had the occasion to try and communicate one-on-one with Linde like this before, but as she interacted with her, Ophilia understood there was a kind of meaning to her every action.

``Thank you and H'aanit both so, so much.'' With her nervousness beginning to untangle, Ophilia smiled sweetly before retrieving a piece of flint from the leather bag. Just when it occurred to her she didn't have any firewood, she spotted some dry sticks and twigs -- Linde must have gathered them while Ophilia had been unconscious. She was able to get a fire going in no time.

She couldn't be sure when the snowstorm would relent, but it would be safe to wait a little while longer like this; still, they needed to figure out their next move before their modest provisions ran out.

``...Linde, are you hungry?''

``\emph{Gauh}.''

``Hmm... is that a yes or a no?'' Ophilia smiled faintly, bemused. She still couldn't quite be sure how much she understood of what she said. H'aanit was regularly communicating with Linde; Linde understood everything H'aanit indicated, and H'aanit didn't have any problem interpreting what Linde was thinking. Still, that didn't necessarily imply that a snow leopard could have a total grasp on human language. The communication between H'aanit and Linde was born of their bond, not of a shared language. Even if the ways in which the two expressed themselves were different, they could overcome the barrier of species between a human and a snow leopard and understand each other completely. Ophilia couldn't help but envy them a little thinking about it. \emph{Still, it's not as though Linde dislikes me,} she thought, gazing at the leopard lying by her side.

She remembered the time, just after the party arrived in Stillsnow, when she and H'aanit had exchanged some words while watching the local children pet Linde. Ever since she'd first laid eyes on Linde, Ophilia couldn't help but want to try stroking her coat -- after all, it looked so soft and so warm... But she had thought that Linde wouldn't permit it from anyone but H'aanit, so she'd always kept that desire in check. When H'aanit told her that Linde liked nothing more than to be stroked and groomed, she was shocked -- and immediately afterwards pet Linde to her heart's content. And naturally, since she had the opportunity now...

``Your white fur really is so pretty. I can see why you're so proud of it,'' Ophilia said as she stroked under Linde's chin. The large snow leopard closed her eyes and purred, apparently enjoying herself. She was still unsure how much Linde knew what she was saying, but she certainly looked somehow boastful. The two continued to pass the time together for a little while longer, Ophilia running her finger's along Linde's soft, warm fur, and Ophilia gradually felt herself beginning to relax before the campfire.

In truth, Ophilia didn't have the time to be leisurely enjoying herself. If it were possible, she'd like to race to Wispermill at once and extract the true intentions of her childhood friend -- the girl she considered her own sister. Indeed, that burning desire was exactly what had thrown her mind into such disarray and distracted her to the point of slipping from the road back to Stillsnow. But with things being as they now were, there was nothing to be gained in getting impatient and rushing herself into further anxiety. Knowing that actually helped to calm Ophilia further.

``I've never had the chance to spend the time alone with you like this before,'' Ophilia murmured as she continued to pet Linde, ``but I'm actually also from the Frostlands, just like you. Staring into a fire on a cold night like this brings back memories from when I lived in Flamesgrace.''

``...'' Linde lifted her head ever so slightly and looked at Ophilia.

``Well, I suppose you've never lit a fire for yourself. But I'm sure looking at the snow all piled up reminds you of home, too, right?'' Still not knowing if anything was getting across, Ophilia kept speaking to Linde.

Ophilia was born in the Riverlands, but Josef had taken her in when she was five years old, and she'd been raised in the Frostlands ever since. The streets of Flamesgrace, blanketed year-round in glittering snow, was unmistakably ``home'' to Ophilia. She'd heard from H'aanit that Linde also came from the Frostlands. It was hard to imagine a beast with that kind of white coat faring well in any other region, so it wasn't all that surprising.

``I wonder, how did you and H'aanit get to know each other in the first place? Raised like siblings under H'aanit's master... Hehe, it's almost like Lianna and me.'' While Ophilia kept petting her head, Linde looked up at Ophilia with only her eyes. Ophilia hadn't necessarily meant anything by that last comment at first, but she found herself whispering, ``It really is just like Lianna and me...''

When Josef had taken in Ophilia as a war orphan, he'd raised her as nothing less than family in Flamesgrace. H'aanit, too, saw her master Z'aanta as a kind of father figure, and just as Ophilia had always had Lianna by her side, H'aanit had always had Linde. Ophilia found herself once again feeling jealous of the two -- that they were able to journey by each other's side.

As Ophilia kept stroking the top of Linde's head, she noticed her ears suddenly twitch. 

``What's wrong, Linde?''

``\emph{Gwauh}.'' The snow leopard growled curtly and got up. Ophilia was able to gather that the noise wasn't one of warning, at least. Linde's gaze was directed towards the entrance of the cave, and Ophilia naturally followed suit.

``Ophilia! Linde! Aren gyt there!'' Along with the yell, a large noise could be heard from beyond the snowstorm.

``\emph{Gau!}'' Linde growled, as though in reply, and Ophilia joined her.

``H'aanit!'' The woman herself, covered in snow and wrapped in furs to protect from the cold, entered the cave and lowered the cloth covering her lower face to reveal a gentle smile. 

```Tis a relief to see thee safe, Ophilia.''

\fancybreak*\pfbreakdisplay

Ophilia had never questioned H'aanit's abilities as a hunter, but she was deeply impressed all over again when she heard that H'aanit had reached the cave just by following the faint tracks Linde had left. After all, in a blizzard like this, just finding the tracks would be a herculean task, let alone following them all the way here. Ophilia was well acquainted with how fearsome snow country could be.

``Thank you so much, H'aanit.'' Ophilia profusely expressed her gratitude, but H'aanit only shook her head\footnote{From here I kind of lost H'aanit's voice -- need to go back and refine}.

``No, in truth I muste thanken you. After all, I have made you joinen me this far.''

``Huh...?'' Ophilia unwittingly replied. While H'aanit placed a small pot over the campfire, she stared into the flames. Into the pot went the ingredients H'aanit had brought with her, and the two made a soup as the snow melted around them. H'aanit stirred the soup with a small ladle and slowly, oh so slowly, began to speak.

```Twas I with business in Stillsnow. Surely your friend weighs on your mind, no? Yet, still you lent me your strength. Had we not your power fighting the dragon of the Whitewood, we surely would haven lost.''

``Has--'' Ophilia dropped her gaze. ``Has it really been that obvious...?''

``I can discern that much -- we're companions, after all,'' H'aanit said, shooting a glance towards Linde curled up by the fire. ``Linde was worried, too.''

``L-Linde, too!?'' \emph{Was it really so obvious that I worried even a snow leopard?} Ophilia suddenly grew embarrassed, but H'aanit only smiled as she stroked her partner's head.

``Indeed. She says when you pet her in Stillsnow, she felt doubt in your fingers.''

``S-she can tell from just that...!? Linde...?''

``When you fell, she moved first out of that concern. It also seems she was quite pleased you praised her fur.'' At those words, Linde sat up and batted a paw at H'aanit, seemingly displeased -- as though she were trying to say, \emph{Don't go telling everyone!} H'aanit soothed her partner with an apology and began serving the soup with the wooden bowls she'd brought. ``How about a simple meal? `Tis a relief you appear mostly unharmed, but `twould be best to warm your body from the inside.''

``O-of course. Thank you.'' Ophilia accepted the steaming bowl and carried it to her lips. The soup was salty and laden with dried meat and beans. She felt a comfortable warmth spread throughout her body. Despite its simple ingredients, the flavor was rich and complex. ``It's delicious...'' Ophilia murmured. ``H'aanit, you're quite the cook, too.''

```Tis glad it is to your t-- Hm?'' H'aanit suddenly seemed at a loss how to respond. After serving herself a bowl of soup and giving some of the leftover dried meat to Linde, she scratched her cheek awkwardly. ``Well, my master did not cook... at first, we woulden take turns, but his work was terribly sloppy, so it became my task alone. Thinking `pon it now, it does rather feel as though I've been cheated.''

``You think so?''

``...So it seems..'' H'aanit made an unpleasant face and sipped at her soup before continuing her story.\footnote{Can insert image here once I have it}

``In the wood, one must be self-sufficient for their food, and with ingredients limited, so strove I to refine what I could maken. Surely Master Z'aanta felt the same and developed for himself some cooking prowess. Then intentionally making a mess of our meals must have just been a way to tactfully shoven the responsibility upon my shoulders,'' H'aanit concluded with a sigh.

``What do you think, Linde?'' Ophilia asked. The leopard opened one eye and gazed up at her from her resting place on the ground.

``\emph{Gau}.''

``You--!'' H'aanit scowled at Linde's response.

``What did she say?''

```Twas something like, `Don't care, it's not my problem.' And then...''

``And then?'' H'aanit grimaced -- apparently she truly, from the bottom of her heart didn't want to say it. Ophilia decided to leave it alone, then, but Linde batted her front paw at H'aanit once again, this time as if to urge her on.

``She said, `But when Master would praisen the taste of your cooking, you seemed fairly pleased, so was it really so bad?' Linde, you knave, did I truly appear so...?'' Linde's response to her partner's stern glare was to simply lie back down and close her eyes with an utterly serene expression.

\emph{They really are just like two sisters}, Ophilia thought. Z'aanta, H'aanit, Linde, and then Z'aanta's partner, the direwolf H\:agen -- to Ophilia, they all truly seemed as close as could be.

``Can Linde understand what I'm saying?'' Ophilia asked, suddenly curious.

```Tis not as though she has perfect comprehension, but the nuance is conveyed. You can gleanen her mood from her disposition, can you not? `Tis similar.'' Then the words she'd spoken before H'aanit arrived hadn't been totally lost on Linde?

According to the hunter before her, magical beasts such as Linde had remarkably higher intelligence and lifespans compared to ordinary animals. They were well-suited for more complex work, and they regularly made their thoughts and feelings known. Thus, a partner such as Linde who had accompanied H'aanit for so many years had naturally picked up some words here and there.

``She is especially familiar with the names of people and places. She understands perfectly the names of our traveling companions, for example.''

``Really...! That's incredible! Even me?''

``Of course. She knows your name to be Ophilia -- and that you, too, were raised in snow country.'' Linde cheerfully supplemented H'aanit's explanation with a \emph{Gau}. ``...And, apparently that you are a discerning woman who can appreciaten her coat of fur.''

``Hehe, it's an honor.'' She was truly quite the clever snow leopard to understand so much. Ophilia was delighted to be able to hear what Linde thought of her. She was reminded all over again that Linde really was a full-fledged member of their party.

As they talked, Ophilia noticed Linde's ear twitch again. The leopard got up, flicked her ears several times more, and turned towards the depths of the cave. H'aanit, too, noticed the shift in her partner's demeanor and grabbed her bow from the cave wall in an instant.

``It seems there is something further in the cave,'' H'aanit whispered as she glanced at Linde tensing up with her fur standing on end.

``...A monster?''

``Most likely.'' At those words, Ophilia went to retrieve her own staff. However, surprisingly, Linde hurried to stop her.

``Linde...?''

``\emph{Gau}.'' Linde barked sharply at the surprised Ophilia. H'aanit grinned.

```Sit back down,' she says. `Let me go assay the danger.'''

``What? But...''

``Fear not, please do as she says. `Tis Linde's way of taking care of you. After all, you've not fully recovered your strength, have you?'' H'aanit she set her bow down and dropped to one knee. She scratched her partner's neck and said to her, ``Very well. Then I too shall remain here with Ophilia. Should there be danger, let us know at once.''

``\emph{Gau},'' Linde barked and turned back around before moving to dash into the cave. However, Ophilia called out to stop her.

``Linde, wait!''

``...?'' Linde stopped and looked back. Ophilia raced over and crouched down to meet her gaze with Linde's. Her staff still resting against the wall, she softly gave Linde her blessing.

``May the Sacred Flame protect you.''

``...'' Linde cocked her head, seemingly puzzled. Perhaps offering prayer to the gods wasn't exactly a familiar part of beast culture. Although apparently still somewhat confused by the strange behavior of the cleric before her, Linde lowered her body slightly as though to offer her acknowledgment before finally turning around for good and running towards the depths of the cave.

```Tis the first time I have seen a cleric offer prayer to a beast,'' H'aanit said when Ophilia returned to the campfire.

``Linde may feel it to be unnecessary... but I don't think it's meaningless to offer her a blessing.''

``No, `tis as you say. Although it may be an unfamiliar practice for Linde and me both, surely your care and concern for her were conveyed loud and clear.''

``Of course.'' Ophilia smiled widely and once more sat back down beside the campfire. H'aanit looked at her and closed her eyes partly, seemingly dazzled.

``You are strong, Ophilia.''

``Huh? Y-you think so...?''

``Indeed. You are a strong, splendid woman.'' Ophilia floundered at this sudden praise, and H'aanit quickly elaborated. ``I do not mean to tease, and I apologize if it sounds so. I was simply recalling what happened in Goldshore -- among those nonbelievers who sought to interferen with your rite, there was...'' As she struggled to get the words out, H'aanit stared into the campfire. ``...your old friend.'' Ophilia felt a sudden sharp pang in her chest.

Just as H'aanit said, Ophilia's Kindling had been stopped by none other than Lianna herself -- Archbishop Josef's daughter, and the girl Ophilia had been raised to think of as her own sister. She had stolen Ophilia's Lanthorn and seemingly made her way to Wispermill.

And that wasn't all. Lianna had told Ophilia of Archbishop Josef's death.

On the way to Stillsnow, the party had taken the opportunity to stop by Flamesgrace. Until then, Ophilia could scarcely believe Lianna's words. No doubt these traumatic events bearing down on her one after another had worn her spirit thin, causing her to lose her focus and ultimately leading to her present situation.

Lianna had stolen the Lanthorn in the hope of bringing Josef back to life. Ophilia didn't know if that was even possible, but at the very least, Lianna believed it was -- and there was someone whispering in her ear, pushing her down that path.

``I believe I canne understand somewhat. After all, I continue to travel hoping to rescue my petrified master. Despite being in a similar predicament, you can still hold your faith in the teachings of the Sacred Flame -- that takes great strength, I feel.'' H'aanit still seemed to have trouble articulating herself. Ophilia could tell she was choosing her words carefully, taking great care to avoid speaking too sharply -- but she understood what H'aanit was avoiding saying directly. She recalled the words of the people who had interfered with the Kindling in Goldshore.

\emph{In the end, he's just another half-wit believer.}

\emph{He can pray all he wants. It's not going to bring him any miracle.}

\emph{What did your church do for your father before his death?}

Finally, she remembered what Mattias, the trader with the Leoniel Consortium, had said to her.

\emph{Sometimes, I even find myself wondering... Do the gods truly exist?}

More than likely the words H'aanit was taking care not to say were something along those lines. It wasn't as though she were decrying the teachings of the Church, though; rather, she was expressing admiration at Ophilia's ability to speak of ``the Sacred Flame's protection'' even after everything that had befallen her -- to H'aanit, that was a kind of strength. 

``I suppose I hadn't thought of it like that before.'' Ophilia let out a quiet laugh. There truly had been no hint of doubt or suspicion in her heart when she had prayed to the Flamebringer Aelfric for Linde's safety.

``Then, believen you that your prayer can bringen about miracles?''

``No, not quite,'' Ophilia said plainly. ``It's not as though I believe my prayer is certain to grant a miracle. That is naturally true of my words to Linde earlier. I believe in the teachings of the Flame, of course, but whether or not that faith can bring about miracles? I couldn't say.''

``Then... why?''

``I suppose it's just as you said earlier.''

``What I said...?'' H'aanit tilted her head, puzzled. Ophilia nodded slightly. When she had prayed to the Flamebringer for Linde's safety, neither Linde nor H'aanit had rejected the unfamiliar custom. Rather, H'aanit had watched Ophilia pray and simply said, \emph{your care and concern for her were conveyed loud and clear}.

``Prayer is nothing but a person's expression of their humble desires -- a wish that something were so. Whether or not those feelings truly reach the Flamebringer is beyond my experience to say. But people still strive to bring those humble desires to fruition -- and in those moments of action, could it not be the `protection of the Sacred Flame' which keeps them moving forward?'' Ophilia continued. ``In their darkest hours, when they have no one by their side, people are afraid to move forward. Even when we push ahead, it isn't certain that we can make our wishes come true. I believe that people need prayer in order to gain that meager courage to keep going.''

``You truly are strong,'' H'aanit whispered softly.

``Really? I mean, don't you yourself keep your master's teachings close, too? I think it's much the same thing.''

``That's... I suppose you have a point.'' H'aanit's expression looked as though she had been momentarily caught off guard before morphing into a gentle smile. Ophilia, too, felt the load on her chest lighten ever so slightly by talking to H'aanit. ``We shall rescuen Lianna in Wispermill. I swear it.''

``Of course.'' Ophilia nodded. ``Z'aanta, too -- I know we'll save him. After all, your master still lives.''

``...Just so.'' H'aanit nodded firmly in turn.

Not long after, a fierce growl echoed from within the cave. H'aanit grabbed her bow and stood in the blink of an eye. She shot a glance at Ophilia, so she nodded and followed suit in gripping her staff.

That was likely Linde's signal -- there was some kind of monster, and they needed to make ready for battle. Linde had told Ophilia to stay put, but if there was danger, she could hardly sit idly by.

``Let's hurry, H'aanit!''

``Aye!'' The two rushed into the cave without a moment's hesitation.

\fancybreak*\pfbreakdisplay

Lying in wait in the cave was a horde of Lizardmen -- a fairly populous race of demihumans in the local snowfield. Across the continent, demihumans had a tendency to grow larger the further one traveled from the midlands, and those living in the snowfield were no exception; and now, several of them, spears in hand, had cornered Linde, who was crouching low and growling at her adversaries.

``H'aanit...!'' Ophilia called out with a hushed voice. ``We need to hurry!''

``Shh... `Tis still alright.'' While hiding in the shadow of a boulder, H'aanit and Ophilia assessed the situation. H'aanit remained perfectly calm as she nocked an arrow to her bowstring. More than likely, Linde had already noticed their presence. If they sent her the signal, the three of them could probably mount an attack in waves, but they ran the risk of the Lizardmen pouncing on Linde all at once.

For now, Linde's intimidation tactics were remaining effective -- the Lizardmen were still keeping their distance.

``If only we could drawen their attention...''

``T-then... how about I become a live decoy?''

``A live...?'' H'aanit unwittingly echoed her words, seemingly perplexed by the sudden suggestion. It was a perfectly sound tactic, of course, but Ophilia and the role of a live decoy seemed to her as though they couldn't be further apart. Whenever the party formed a strategy like this, such a role almost always fell to Therion or Olberic. Even if Ophilia was more than accustomed to battle, she wasn't exactly a brawny warrior -- not to mention she had been passed out in the snow not even a couple hours ago. Her recovery still wasn't certain, and if it could be helped, H'aanit would prefer not to put her in harm's way, but...

``You're not the only one who wants us to all make it out of this alive, you know,'' Ophilia said, gripping her staff.

``...Of course.'' \emph{She truly is strong,} H'aanit unconsciously murmured to herself. It wouldn't do to be overprotective. Ophilia was just as capable a fighter as any of their companions. She had vowed not only to rescue her own childhood friend, but also to save H'aanit's master. ``Then just a moment shall do. We needen only a single opportunity. Linde and I shall step in ere we allow their spears to reach you.''

``Got it.'' Ophilia nodded firmly. Keeping her body low, she stealthily emerged from the shadows and made to cut across the passage before catching the attention of one keen-eyed Lizardman among the group surrounding Linde.

``\emph{Gyageeh! Geeh!}''

``\emph{Gyauh!}'' The Lizardmen began a commotion at once. Using her staff as a support, Ophilia quickly rose to her feet and turned to face them. Her gentle features elegantly drawn tight, she braced for their attack, holding her staff like a spear.

However, the one most surprised by this turn of events ended up being Linde, who shot a momentary reproachful glance towards H'aanit's hiding place in the boulder's shadow. 

\emph{Don't look at me. `Twas her idea.} H'aanit replied in her head as she kept an eye on the situation. Before the Lizardmen could make a move, Ophilia began chanting an incantation. H'aanit gave her partner the signal -- \emph{Close your eyes and get down.} Just then, Ophilia raised her staff and cried out,

``\emph{May the Sacred Flame shine forth!!}'' A blinding light flooded the cave in an instant. One of the Lizardmen who had tried to approach Ophilia let out an especially loud yelp. The Sacred Flame was well-equipped to smite the impure with its holy light, but in such a dark, cramped space as this, it also happened to double as an excellent smokescreen.

``Now, Linde!''

``\emph{Gau!}'' Just as the light flickered out, H'aanit and Linde made their move. H'aanit shot several arrows at once towards the cave ceiling. The arrows cut a beautiful arc through the air before hailing down upon the heads of the Lizardmen. Already dazzled by Ophilia's sudden flash of light, they now found themselves on the receiving end of H'aanit's rain of arrows. Meanwhile, as though she knew where each and every arrow would land, Linde weaved through the onslaught and launched herself at the panicking Lizardmen, extending her claws and baring her teeth. As though she were cracking a whip, she extended her long, supple tail and skewered a Lizardman behind her.

Only four Lizardmen remained. One of them, having dropped its spear, barreled towards the nearby H'aanit. Cornered, H'aanit swapped her bow for her hatchet and deftly leapt backwards. She chanted a spell passed down in S'warkii, and the air crackled with a burst of lightning. The Lizardman recoiled, and she snared it with a leghold trap, utterly arresting its movement. As her opponent writhed in panic, H'aanit cracked her hatchet against the crown of its head.

\emph{Only three left!}

However, those three had already run from H'aanit and were now moving in Ophilia's direction.

``Linde!'' H'aanit shouted. Her partner leapt into action at unthinkable speed, but still only managed to take down one of them. H'aanit nocked an arrow to her bowstring once more and aimed for another, but despite her best efforts, she couldn't land her shot.

Yet not a trace of fear could be found in Ophilia's eyes -- she simply gripped her staff tightly in her hand and held it aloft like a supplication. 

``\emph{Aelfric, Bringer of the Flame!}'' In that moment, Ophilia's own words played back in H'aanit's mind. She had said that she didn't invoke the names of the gods in order to bring about miracles; that prayer was simply an expression of desire, with the goal of squeezing out that last bit of courage necessary to keep people moving forward.

But maybe, just maybe, could it be that what people call a ``miracle'' was indeed that very courage -- that power to stir people's very hearts?\footnote{help. ``very'' has stopped looking like a word} As H'aanit wondered to herself, before her very eyes, Ophilia was faintly wreathed in flame, with a color greatly resembling that of the Lanthorn of the Kindling she had so reverently carried this far. Even though the cave should have been cut off from the outside world, H'aanit felt a sensation well up much like a gust of wind.

``\emph{Let the Flame guide you true!}'' The moment Ophilia's eyes shot open, dazzling light erupted all around her. Power surged through H'aanit's body. She couldn't be sure of the exact mechanism, but there was no question it was due to Ophilia's words just now -- the strength budding in her body now was, without a shadow of a doubt, thanks to Aelfric's Auspices.

With unprecedented speed, H'aanit loosed an arrow, effortlessly vanquishing of the Lizardmen as another fell to Linde's fangs and H'aanit nocked another arrow in a single fluid motion.\footnote{I want this to feel fast and fluid but I worry it just reads like a runon} The instant she fired her second shot, Linde, too, twisted her body and launched herself. The final Lizardman was run through by H'aanit's arrow and Linde's tail alike.

``\emph{Gah...!}'' In its death throes, the Lizardman coughed up blood, staggered forward with its spear as a support, and collapsed to the cold cave floor.

``Ophilia!'' ``\emph{Gau}!'' H'aanit and Linde raced towards Ophilia at once.

``Are you hurt!?''

``No, I'm perfectly alright.'' Ophilia smiled weakly, and H'aanit and Linde finally relaxed. It seemed there really was nothing wrong. H'aanit found herself thinking, \emph{Is it over?}, but it seemed there was yet more for Ophilia to do. She softly crouched before the corpse of the fallen Lizardman, closed its still-open eyes, and offered a prayer.

``I pray that the merciful Flame grant peace to their souls...'' 

H'aanit met Linde's gaze and nodded. They had seen something like this once before, when they had journeyed to the Sunlands to take care of some of Olberic's business. After the party defeated the horde of monsters attacking the village of Wellspring, Ophilia had prayed for the repose of their souls. Come to think of it, those monsters, too, had been Lizardmen. 

H'aanit had admired her for that -- although Ophilia's life as a cleric differed greatly from her own, she shared the hunter's ideal of treating any and all life with the same reverence. Even if it wasn't certain how much stock monsters held in a prayer to the gods, Ophilia could offer it all the same simply because those monsters, too, were alive -- just as H'aanit had said before, she was truly splendid.

\emph{Aha}. Linde sat down by H'aanit's side, and as H'aanit stroked her head, she felt everything suddenly snap into place. ``So that's why you love her too, is it?''

``\emph{Gau}.'' H'aanit wondered what it was like for her partner, just as much of a ``beast'' as those Sand Lizardmen, to see Ophilia pray for them. Perhaps it would be insensitive to even ask.

``I'm all done, H'aanit. I'm sorry to make you wait.'' Having finished her prayers, Ophilia returned to H'aanit and Linde.

```Tis no worry.'' H'aanit nodded. From the moment they caught sight of Linde, there was probably never any chance of avoiding a fight with these Lizardmen; after all, they had no hesitation in attacking humans. Still, it wasn't as though she had killed them for fun or enjoyed doing it. Using what one can of one's quarry is a hunter's way of paying respects to their fallen prey -- in this case, that happened to be the Lizardmen's dwelling. At the same time, by praying for their souls, Ophilia was carrying out a cleric's way of paying respects to the dead. ``Thank you, Ophilia. For praying for them.''

``Of course.'' Ophilia gave a broad smile at H'aanit's words.

\emph{A prayer is a wish}. Such sweet words -- surprising even herself, H'aanit wondered if she would ever find herself praying to the Flamebringer. If she did, she hoped she could take those words to heart.

\fancybreak*\pfbreakdisplay

After that, they spent a little while stoking a campfire near the mouth of the cave. Wrapped in blankets H'aanit had brought and nuzzling against Linde's warm fur, H'aanit and Ophilia slept in shifts. As dawn broke, the blizzard had stopped entirely, the light of the sun shining from the cerulean sky reflected dazzlingly off the silver snow.

``Heeeey!''

``Miss H'aanit! Miss Ophilia!'' From the white world outside, someone's voices rang out -- the dearly familiar voices of their companions. Hearing those voices, Ophilia was roused from her dozing. 

``Those voices...''

``It would seem they've come to pick us up.''

``Oh, thank goodness...'' The horse-drawn sleigh carrying their companions finally came into view. In the coachman's seat sat the seer Susanna's bodyguard, Alaic. As he confirmed their safety, relief spread across his stern expression. Tressa and Alfyn stuck their heads out of the sleigh and waved broadly.\footnote{how do you indicate the Size of a wave. in jp you wave bigly} Ophilia waved back with a smile. Shooting a furtive, sidelong glance at her, H'aanit asked,

``It may be a little late to ask, but... will you be alright, Ophilia?''

``Huh?'' Ophilia was caught off guard by the question at first, but quickly realized what H'aanit was asking. She nodded right away. ``Yes, I'll be alright. I'm sorry to have worried you and Linde.'' H'aanit was asking about Lianna. Ophilia had been worried about her all this time, and even if it was Ophilia's problem to solve, H'aanit had been frustrated at her inability to offer any help. ``It's not as though all my worries are gone, though. All this time, I had no idea Lianna had been pushed so far to the brink. I truly regret not having been able to understand how she was feeling.'' H'aanit listened silently as Ophilia spoke. ``I did find myself feeling a little jealous of the bond you and Linde have, though.''

``You mean how we can understand each other even without a common tongue?''

``That's right.'' Ophilia smiled. ``But after spending the night in a blizzard with you two, I understand it now. Your bond is extraordinary, but at the same time, it isn't. You share an understanding, but there are still things you don't know about each other. In that way, it's just like Lianna and me.''

``Just so.'' H'aanit nodded. It wasn't uncommon for the beast-taming hunters of S'warkii to hear similar things from outsiders envious of their ability to form so strong a bond of trust with their beasts. However, those outsiders were prone to mistaking that relationship for something exceptional beyond just crossing the barrier of species. There was, of course, a firm bond and great trust between H'aanit and Linde; however, that was all. Their thoughts and feelings still needed to be conveyed to each other in order to be known. To borrow Ophilia's words, it was extraordinary, but at the same time, it wasn't. Their bond was no different from those among humans; nor, for that matter, from that between Ophilia and Lianna.

H'aanit traced her mind along the trajectory of that thought. H'aanit could understand how Lianna felt -- when Z'aanta had been turned into stone by Redeye, H'aanit had done everything in her power to seek out a way to save him, and was lucky enough not only to find one, but to find one that was within her power to achieve.

What if she hadn't been so lucky, though? What would have become of her? That was a difficult question to answer. All she could say was that even if she was unable to find a way to save him, at least she still had Linde by her side. When she first saw her petrified master before her eyes, it was only because her partner was with her that she could stay calm -- and if she had lost her composure, surely Linde would have been able to keep her in check.

Just as H'aanit needed Linde, surely Lianna, too, needed Ophilia. In that case, H'aanit would do everything in her power to see that Ophilia reached Wispermill safe and sound, and if Ophilia needed help even after that, she would happily lend her strength.

``We \emph{will} rescuen Lianna, Ophilia.'' The promise they had exchanged in the cave naturally fell from her lips once more. ``I swear it.''

``Yes, of course.'' Ophilia again nodded firmly at H'aanit's words.

``\emph{Gau}.'' Linde, who had stayed silent all this time, growled brusquely. H'aanit scrunched her face. Ophilia looked at their faces in turn and cocked her head.

``What did Linde say?''

``W-well, that's...'' H'aanit, taken aback, glared at Linde. Linde jutted her chin out in response, as if to say \emph{Go on, tell her!} H'aanit scowled as she translated faithfully.

```Sure is a pain having such a foolhardy sister, isn't it?' ...she says.''

``Oh, my.''

``Linde, did you call me \emph{foolhardy}? Compared to Master, I--!'' H'aanit began grumbling in earnest, but her partner made no pretense of lending her an ear. Instead, she simply stared at Ophilia, who in turn smiled softly as she met Linde's gaze.

``I've never once thought of Lianna as a `pain.' Surely you feel the same way about H'aanit, don't you?''

``\emph{Gau}.'' The leopard raised the corners of her mouth, baring her teeth ever so slightly, then turned her face away in a huff. 

Even without H'aanit's translation, Ophilia understood the meaning of that last growl. She stroked Linde's prized fur, a gentle smile on her face.
\printendnotes