\begin{flushright}\emph{Month of Sealticge, Week 1, Windsday}\end{flushright}


\emph{So much time has passed already since I first set out on my journey. I left home all alone, but before I knew it, it was like I'd become part of a big family! Every day is so lively.}

\emph{Professor Albright and I seem to get excited about a lot of the same topics -- the Flatlands and the Coastlines are right next to each other, after all. Professor Albright isn't a really sentimental kind of guy, but it's not that he's cold or distant, really. In fact, his unusual level of composure and maturity has been a huge help on more than a few occasions.}

\emph{That said, though, there are some things about him that remain a mystery to me... It all started on our way to Stonegard, a few days after we left Atlasdam ---} 
\\

 The eight of them varied wildly in birthplace and upbringing alike, making their journey unconventional, to say the least. To start with, the only ones among them that could really be considered experienced "travelers" were Therion, the wandering stranger, H'aanit, ever so particular about their camping arrangements, and Olberic, the seasoned warrior. As for the others, they had hardly left their hometowns, much less gone on a grand journey like this. 

"If we proceed at this rate, we should reach the Coastlands by nightfall," Olberic announced, spreading out the map as he walked along the main road.

They were proceeding faster than normal today, making good time to leave the Flatlands before long. It was with all this in mind that H'aanit, walking in the middle of the group's formation, turned to look back at the rest as she muttered, "Everyone's tenacity far outstrippeth my expectations." They'd been walking nonstop for a considerable time since departing Atlasdam, yet she'd not once felt even short of breath. Linde, her snow leopard, sat down by her side with an unbothered expression.

"Quite so. It seems neither Alfyn nor Ophilia have known little of travel at all, but despite that they've kept up quite nicely, without any show of complaint." Leaving the others in the back a few paces behind, Cyrus expressed his agreement as he approached. He, too, had managed to match their steady pace without even a hitch in his breathing. As for the rest of the group, Primrose and Therion led the group with Olberic, while Tressa, Alfyn, and Ophilia trailed behind. H'aanit raised her eyebrows, bemused.

"Thou art no less included when I say 'everyone,' Cyrus."

"Oh, is that so?" he asked breezily, seemingly not taking any offense. "I'm sure you have an image in your mind of scholars cooped up in their studies, doing naught but reading dusty tomes all day. Naturally, that kind of thing is important, but as for myself, I'm not the kind of person to neglect the value of field work, you know. One's body is a precious resource. My muscles are hardly carved from stone, but I do believe I can handle a little walking."

"Speak'st thou true, I wonder..." H'aanit murmured as she craned her neck to look past the back of the group. There, further down the slope, a small figure with a massive bag strapped to her back continued to climb, weakly gasping for air. It was Tressa Colzione -- though a bona fide merchant in both willpower and way of speaking, she still hadn't quite grown out of her teenage looks. Right behind Tressa were Alfyn and Ophilia, who called out in concern as they kept moving.

"Tressa, if you'd like, I can hold your luggage for a bit...?"

"Grrrr.... I'm alright, Ophilia....." Tressa gasped, her voice strained through gritted teeth. "Don't.... Don't take us merchants lightly, you know...! A hill... like this... is \emph{nothing!}"

It was a beautiful day, and the travelers and road before them baked in the Flatlands sun. Sweat beaded on Tressa's face as she continued to limp down the main road step by step.

"She's got quite the burden there, hasn't she?" Cyrus mused, stroking his chin as he gazed back at the little merchant. "It'd be easy to think she isn't particularly strong, but judging from the size of it, carrying that baggage of hers all this time must be no small feat." One's eyes couldn't help but be drawn to her luggage, even from such a distance. She'd strapped those bags to her back ever since she left home in Rippletide. It was natural that she had far more to carry than her companions, given she also had to carry everything she had for sale. They'd proposed she borrow a mule to help carry at least some of it, but she insisted on carrying it all on her lonesome. If she wanted to carry her own merchant's burden by herself, there wasn't much any of the others would say to object. Cyrus, as a scholar, and H'aanit, as a hunter thought perhaps someone should object. The group of eight carried on amidst this strange dynamic.

"H'aanit, I propose we take a short rest here. What say you?"

"Aye, perhaps that wouldt be best." She looked towards the front of the group and nodded slightly as she watched Olberic fold up his map. This wasn't Cyrus offering his wisdom as a scholar, nor H'aanit consulting her expertise as a hunter. This was simply two traveling companions watching Tressa, against all odds, take that last laboring step up the slope and offering her time to catch her breath at last. Perhaps at that proposal, at least, the others would be in agreement.

"Finally... I made it!!" A wide grin split across Tressa's whole face as she raised her arms in celebration of her achievement. "This is it... it's actually the top of the hill! You can see the whole ocean from up here! It's so beautiful... Alfyn, Ophilia, come see!"

"H-hey, Tressa!"

"Tressa, maybe we should rest a little first..." But seeing the girl's exhaustion begin to melt away into pure excitement, Alfyn and Ophilia nonetheless ran to catch up to her. Cyrus, watching this lively scene play out before him, merely shrugged.

"Do you think our worries were perhaps unfounded?"

"Certainly not. 'Tis absurd to think I would not agree she worketh herself too hard. The sooner we maken camp, the sooner she can taken some well deserved rest."

"Quite so." Cyrus nodded at her. It was hard not to feel some kind of pride, watching Tressa excitedly show the other two the scenery from the top of the hill. Cyrus remembered something. When they had first departed Atlasdam, Tressa had told him she had come up from Rippletide, taking the northern road. In that case, she should have passed across this slope once before on her own already. It musn't have been a pleasant climb then, either, yet it seemed she'd nonetheless discovered something valuable on the way -- namely, the picturesque scenery before them. Past the plains and beyond the hill were the Coastlands from which Tressa hailed, a land of salty sea breezes and the roar of the waves, of endless clear skies and the deep blue ocean, where the wind carries the aroma of the shore as you approach. The profound impact of seeing this scenery for the first time must have been something for her and her alone. Now that he thought about it, Cyrus realized he wanted to know more about the reason she had set off on her journey in the first place. He, too, knew the thrumming and ringing in one's chest that comes with crossing the threshold into worlds yet unknown, how moving and exciting that sense of discovery could be. He walked over to Olberic, who stood in the shade of a tree, unfurling his map to study it once more, and asked, "Olberic, have we made good progress?"

"Indeed. In fact, we may even be going somewhat too fast. I believe we should slow our pace a little."

"I see. I was thinking of proposing the same myself, actually."

"Well, when you see how Tressa is faring..." Olberic's line of sight settled on Tressa, who was now sitting on the ground, monolithic luggage still strapped securely to her back. She had been practically jumping up and down with excitement a moment ago, but now she was making no effort to hide her exhaustion. Taking her into account, as well as the others who were not yet accustomed to travel, it was a reasonable plan Olberic had proposed. Looking at the group as a whole, though, there wasn't any urgent need to worry too much about their pace from here on out.

"Olberic, do you perhaps know anything about why Tressa began traveling in the first place?"

"Hm? Now that you mention it, I don't believe I've ever asked her. I get the impression that it differs from the reasons you and I have, though. I have the impression the experience of traveling itself seems to be part of her goal."

"That very well may be. I know she frequently refers to a journal she received from someone, but I don't believe it draws her towards any particular objective." To this, Olberic simply offered a "Hm," as he closed the map once more.	

"I take it you haven't simply asked her directly either, then."

"That's right. I can't help but find myself taking some interest in it, though."

"If you're so curious, just go on and ask her. That would save you a good deal of time rather than trying to do your usual roundabout method of investigation."

At this, Cyrus stopped. This idea was so brilliant that it was as though he had been slapped upside the head with it as he nodded with deep satisfaction.

"I do believe you're on to something. All this superfluous enquiry is somewhat of an unintentional bad habit of mine, I believe."

"Have you even the slightest self awareness...?" Olberic muttered, too quiet for Cyrus to hear.
\newline

Just as Olberic predicted, they were able to cross into the Coastlands well before nightfall without any real delay in their overall itinerary. They made camp on a spot by the side of the main road, accompanied by the sound of the waves. As each of the companions passed time in their own ways, night finally came.

"\emph{Month of Sealticge, Week 1, Lightsday... I'm back in the Coastlands for the first time in forever!}" Outside the tent, with the aid of the light of a lamp, Tressa scribbled furiously in her journal. "\emph{The view of my hometown I could see from the Flatlands was so beautiful...}" At this, her hand stopped, and she looked up. When they'd returned back to the area she'd grown up in, the first thing she was surprised by was the sound of the waves beating against the shore over and over again. "\emph{I can't believe how loud the waves are!}" All that time in Rippletide, she'd never realized. Spending such empty, pitch-black nights in the Coastlands truly made one feel as though they were being swallowed whole by the sea. Thinking about her time on the road after leaving home until she eventually arrived in Atlasdam, she realized that sensation was rather familiar. "\emph{At first, it was really scary! Until I reached Atlasdam, I was all on my own.}" Countless times she'd had dreams of the waves along the shore catching her unawares and taking her out to sea. Each time she awoke, she dragged her sleeping bag another five steps away from the beach. 

Tressa looked down at her journal once more and continued writing, committing everything she felt, everything she thought, everything she said during her time here to paper one by one. "\emph{But now I'm traveling with so many new people, and I don't feel so uneasy at all anymore...} There!" Inside the tent were Primrose, H'aanit, and Ophilia, while Olberic, Therion, and the others were in the men's tent a bit away. She wondered what it was that led each of them to keep traveling. The beginnings of each of their journeys couldn't have been too long ago, but by now she'd already forgotten the concrete reasons. Yet before she knew it, one of them, then two began walking by Tressa's side, until somehow in between the eight of them had become such a big family. Each and every one of them had been an invaluable companion to her.

Alfyn, worried about her after walking nonstop so long, had prescribed Tressa a salve infused with medicinal herbs to help with the fatigue. Combined with a cold compress, he assured her it would ease her sore, aching muscles. At once, she'd applied the medicine to her calf and wrapped a cool cloth around it just as he told her. The feeling of the cloth, chilled by the sea breeze, was wonderful. She decided to write about that, too: "\emph{Alfyn still told me he wouldn't take any money for his medicine today.}" Each time Tressa tried to propose a price she'd pay for his prescriptions, he gently declined. She tried more than a few times, but no matter how many times she told him, "I'm a merchant! There's no way I can just take an apothecary's medicine without paying for it!" his reply would never change: 

"In that case, I ain't an apothecary. Consider it a personal gift from me to you, Tress." She was yet to push past his unshakeable goodwill and get him to take even a single leaf. Still, she understood that refusing payment like that was just what Alfyn believed in. 

"\emph{Maybe stuff like that is why Alfyn started traveling -- he wants to help people all over the world with his medicine.}" Without realizing it, Tressa's scrawling across the aged paper of her journal had moved to the topic of her companions. She wrote about Olberic and his journey to confront his former brother in arms, about H'aanit and her search for her master who disappeared without a word. "\emph{Everyone's got their own goals to follow. As for me...}" Tressa's pen, which had so fluently been soaring across the page, came to a stop. "As for me... I'm... Er...." \emph{What about me?}

Tressa set down her pen. She crossed her eyes and grimaced, looking up at the sky, then looked back down to scowl at the ground. No matter how much she moaned and groaned to herself, it never came to her. \emph{The reason I'm on this journey.} Naturally, Tressa had one as well. Yet when she lined it up with the others' it felt so... insignificant, almost childish. It wasn't laden with conviction or ideals, or even any kind of special emotions. She wanted to know what was beyond the walls of her hometown, to follow in the footsteps of the nameless traveler whose journal he'd left behind, but that yearning for the open road felt like it was all too commonplace a dream. She tried embellishing it in her mind, qualifying it with all kinds of fancy words and a degree of braggadocio, but still it never felt right. Then, while she was turning this all over in her mind,

"Oh my. You're still awake, Tressa?" 

She looked up at the sound of a familiar voice. The face of a man emerged from the pitch black of the night, illuminated in the dim lamplight; a man whose age was difficult to discern, as his youthful looks clashed with his unusally composed presence -- Cyrus Albright. As for his reason for taking to the road, Tressa had actually asked him directly. Though his journey had been short, he had a precise goal clear in his mind: He sought to track down \emph{From the Far Reaches of Hell}, a tome that had disappeared from the library of the Royal Academy, in pursuit of his ideal that knowledge ought to be spread far and wide, shared with all people. Tressa thought this was a reason more than worthy of praise.

"Er... I just got wrapped up in writing in my journal." She decided to answer truthfully as she shut the book resting on her knee.

"I see." Cyrus' gaze dropped for only a moment down to the journal, then back to Tressa. "Do you mind if I sit?"

"Oh, go ahead. Sorry it's not exactly the most luxurious seating." With a small "Well then," Cyrus sat himself near Tressa on a reasonably-sized boulder.

"Surely anything you're writing about doesn't warrant such deep forethought. It's best to just write it down precisely as it is."

"As it is...?"

"That's right. Just as it is, with no need for any flowery language or embellishments. Particularly if you're simply writing for yourself. The most important thing, Tressa, is that you write down your thoughts in exactly the same way you have them..." At this, Cyrus suddenly grinned. "...Even that, though, can still be quite a challenge. Might I perhaps be of some assistance in helping you organize your thoughts?"

"Um..." Tressa hesitated for only a moment before making up her mind. This was Cyrus Albright, after all -- a man who commanded attention at the Royal Academy with the tip of his teacher's pointer. There wasn't a better person in the world she could consult with. An audience with him was worth more than what money could buy. She forced herself to tuck questions about a fraught business proposal of hers into the recesses of her mind and laid her actual worry bare: that she worried that her own journey lacked the same kind of conviction and earnestness of her companions'; that from the moment she departed her dream was one that lacked anything special, that just about anyone could have. She didn't want to come across as self-deprecating, but it was at that point in her thought process that she could no longer put things into words.

"I see." Cyrus nodded slightly and stroked his chin. Amidst the silence broken only by the sound of the waves, the dim lamplight illuminated Cyrus and Tressa's faces dazzlingly.

"Professor, you set out to go find that lost book, right?"

"That's right. Of course, it also happened that I found myself to be no longer needed at the Academy... Well, I suppose you could just as well consider either of those to be my reason for departing Atlasdam." There was nothing on his face to suggest he felt any anger or regret about the situation. "Tressa, I believe you flattered me by calling my own reason >more than worthy of praise,> is that right?"

"Erm... yeah." Tressa gave a small nod. "It feels like it suits you too. Holding fast to your ideals, it's so... grown-up."

"I also happen to be some twelve years older than you. It would be unbecoming of me to set a poor example." He laughed drily, then continued, "But following one's ideals doesn't just take one form. I can see from how you conduct yourself that there are certain principles of your own you adhere to, and in them I respect you a great deal."

"Really?"

"Really. ...But I suppose that naturally it's difficult to simply take my word for it at face value." Gazing up at the star-filled sky, Cyrus continued on to the main topic at hand. "If I may, there's actually something I wished to ask you, Tressa."

"Me, Professor? What is it?" Her eyes widened -- it seemed she felt she couldn't possibly have anything to offer him except perhaps her expertise as a merchant.

"As a matter of fact, it was what your reason for going on such a journey might have been. A moment ago, you said you felt it wasn't so grand as the motivations of Olberic and the others, but I don't believe I ever asked you precisely what it actually was, have I?"

"I don't think so..." Tressa scratched her cheek. She wanted to talk, but she was too embarassed to put it into words; at the very least, this wasn't something she was very proud of. But she'd already agreed to talk to him, so keeping quiet now was out of the question.

"It's really nothing important. But there was something I wanted to see."

"Something you wanted to see?"

"Mhm." Tressa clutched her journal as she stood and took in the scenery around her, cloaked in the curtain of night. Lit only by the faint stars and the light of the moon, it was hard to see the deep black ocean clearly. In that silent world, the horizon over the water dissolved in the thick darkness, and the sky and the sea and the vast land around them all blurred together. There was only the sound of the waves to accompany the passage of time, to tell Cyrus and Tressa that these really were the Coastlands.

"I wanted to know what was beyond that horizon." Tressa had been born and raised in the port town of Rippletide. In comparison to those she traveled with, nothing terribly dramatic had ever happened to her. She had lived a life that anybody could have had for eighteen perfectly normal years. Every day, she woke up and learned the fundamentals of commerce from her parents, hearing those same waves and bathed in the sea breeze. Yet one day, staring at the water past the port, that question finally occured to her. \emph{What in the world could be on the other side of that water?} And so, that was the reason Tressa began her journey. Certainly there were ways for her to learn of the world beyond without needing to leave home, but not a single one ever left her satisfied. When she first set foot in the Flatlands and looked back upon the path she'd traveled, that uncertain curiosity solidified into conviction. Beyond that, there was no other reason she'd begun her travels. Of course, what motivated her to leave at all was Captain Leon and the journal he'd given her -- the words written on its aging pages kindled her desire enough to give her that final push.

"I see." Cyrus closed his eyes and nodded deeply. Tressa worried she'd disappointed him. Cyrus wasn't the kind of person to thoughtlessly deride what other people thought, but she truly felt she hadn't said anything so dramatic as to provoke any kind of special emotion.

"So, Professor, I really think that--"

"That's a marvelous reason, isn't it?"

"H-Huhh?" His response startled her so much she accidentally raised her voice. "B-but Professor, that really is all there is to it... Going on such a dangerous trip with such a vague reason in mind just feels so childish...isn't it?" Yet Cyrus' face showed every indication he was being serious.

"If I may, Tressa. When we have doubts about something, when there is something which we desire to know -- that is the first step on the stairway to the door to scholarship. Moreover--" As he spoke, his words became tinged more and more with passion. Tressa had only been at the man's side for a brief time, but that was enough to know full well how his voice became packed with energy when he was confronted with a topic he cared deeply about.

"Moreover, those doubts encompass a great, great many things. Yet the people who are able to open that door -- in other words, those who depart on the quest for that knowledge -- are very, very few. Tressa, when you, in pursuit of your own curiosity, took your hand and opened that door, you placed your foot across the threshold dividing the known and the unknown. As a scholar myself, I cannot help but express my marvel and admiration in face of your motivation to journey on." Cyrus' expression as he heaped on this praise was unbelievably earnest. Tressa squirmed a little, and couldn't help but feel a bit embarrassed.

"I don't know about all that, ehehe..."

"I'm certain of it. Tressa, your inquisitiveness truly is well-suited to scholarship." Cyrus was not a man given to flattery, certainly, but being confronted head-on with such lavish compliments was almost too much to bear, not to mention being told she was "well-suited to scholarship" by a man who stood as a professor at the Royal Academy in Atlasdam.

"I mean, I'm just a merchant..." She tried to protest, but she couldn't help but break into a grin. "But if you say so, Professor, I'll hardly take offense!"

"Wonderful. Do you think you'll be able to keep writing from here?"

"Yes, thank you so much, Professor!" Cyrus smiled gently listening to Tressa's earnest words of gratitude as she placed the journal on her knee and opened it once more. After hearing Cyrus' words, she once again sorted out her emotions. She tickled her forehead with the feather of her pen as she paused to choose the right words, then dipped its nib in ink and set it racing against the page. "\emph{As for me, I set out to learn about what's beyond the horizon that I've been fascinated by for so long.}" She didn't care if anyone praised her for it. It didn't matter if anyone else approved of it -- why Tressa left on her journey was something that belonged to Tressa and no one else. Nevertheless, though it may have been just the exhaustion of the long journey, something about Cyrus' words tugged deeply at Tressa's heart. "\emph{I still haven't found the answer yet... But I hope I can pack this journal with all the time before I do.} ...Aaand, done! Mhm, not bad at all!" Tressa held the journal up proudly over her head, pages spread open. Cyrus nodded contently towards Tressa, seeing her look up from the book.

"Hey, don't you know it's rude to read other people's journals, Professor?"

"Ah, my apologies. In my defense, I wasn't reading your journal, but rather watching how swiftly your pen darted across the page. You had the most wonderful expression on your face, you see."

"That so..."

"I certainly thought so. I'll confess I can't help but wonder of what you were thinking, of what you were writing, but I know prying into other's business is a poor habit of mine. Whatever the contents of your journal may be are for your eyes only."

Tressa closed the book and put it back into her bag. "But Professor, I thought you hated people who kept knowledge all to themselves? You said something like that to me once, I think..." She'd blurted out the question without thinking, but Cyrus merely responded with a "Hm," offering neither denial nor agreement. 

"It's true that I believe knowledge is something that should be open to all... But what is recorded in that journal of yours is not >knowledge,> but rather >experience.> That experience is not something that can be deciphered simply by reading your notes. Not to say that that itself can't be valuable in scholarship, however."

"Hmm.... I think kinda get it... But I also kinda don't."

"Really? In that case, allow me to explain this in a way that may be perhaps more understandable..." As Cyrus retrieved a stick from the ground, preparing to make ready use of the ground in place of a chalkboard, Tressa frantically rushed to intercept him; this was a clear sign that they were on the precipice of a lecture that may not be able to be stopped once started.

"Oh, I- I think I get it now, Professor! All of a sudden, it just clicked! No need to worry about it!"

"Is that so? But don't you want to know more?" Tressa's scowl would have been truly spectacular, had Cyrus not been so engrossed in diagramming in the sand.

"There's a most wonderful book from a scholar by the name of Susanna Grotoff, you see..."

"P-Professor! Come on, it's night already! It's really getting late, so maybe we should call it... Right!?"

"...I suppose you may be right." The relief Tressa felt in her chest as Cyrus finally looked up from his makeshift chalkboard was palpable.

"At any rate, the most important thing is that our conversation was able to be of service to you, Tressa." With the air of a teacher dismissing his class, he set his stick back on the ground.

"Mhm. Really, you were a huge help. Thanks, Professor."

"No need to thank me. It was privilege enough to get to you that much better." Cyrus stood as he spoke. "Now then, you should go get some sleep. We're getting back on the road bright and early tomorrow morning."

"Good idea. You too, Professor."

"Actually, I believe I'll be awake just a moment longer. I thought I'd roam around the area a bit, you see."

"Huh??" For Tressa to respond in such a way to Cyrus was natural. That simple "Huh??" contained a multitude of meanings: "Why on earth??" and "Just go to bed already!" for instance. 

Yet in Cyrus' ever indefatigable fashion, he simply said, "It's been quite some time since I was last in the Coastlands, you know. There's an endless amount of things I wish to examine, but I wouldn't dare slow down the pace of our travel. Thus, I can only take the time to investigate to my heart's content in the middle of the night..."

"I-I see..."

"Nevertheless, you should go rest as soon as you can. If you allow your fatigue to persist into tomorrow, it would put all of Alfyn's care to waste." Tressa looked at the cold compress Alfyn made with so much care for her.

With no more than a "Well then," Cyrus stood once more. It seemed he was serious about going on his nighttime excursion -- and alone, at that. It wasn't that the area around Rippletide was dangerous, really -- Tressa had managed alone fine, after all -- but she couldn't help but wonder what on earth he was going to investigate at this hour. Just as Cyrus began to walk away, Tressa grabbed at the hem of his cloak.

"Hold on a second, Professor!" Naturally, he looked down at her with surprise. She looked back up at his face, illuminated by the lamp and the starry sky.

"What's wrong, Tressa?"

"I'm going too!"
\newline

Why had Tressa said such a thing? Even she wasn't quite sure. The idea that she was worried about Cyrus wasn't particularly convincing. If that were the case, it would be all the more reason for her to stay behind and have someone like Olberic or H'aanit accompany him. If she had to admit the real reason she'd blurted out "I'm going too!" like that...

"Are you curious?" Tressa tilted her head, watching Cyrus from behind. To be honest, she thought seeing what Cyrus found interesting about her native Coastlands was interesting in and of itself; on top of that, though, she'd never actually walked through the shores near Rippletide at night before. The idea was somehow exciting.

In other words, yes, she was curious. She hadn't expected that inquisitiveness Cyrus had praised in her just a moment ago to manifest itself at a time like this.

Cyrus turned back to face Tressa and asked, "Won't you stay behind?"

"I'm okay. Really, I don't feel so tired anymore."

"Is that so? I truly do not wish to potentially put you in danger. If you are still ailing, I'd prefer that you be honest about it." She didn't get the sense he was unnecessarily needling her; this really was just Cyrus looking after her health, assuming the role of the adult in the room. Tressa wondered if he showed every single one of his students at the Royal Academy this much care. \emph{I can see why he was so popular...} Cyrus' real tragedy was that though he excelled at demonstrating such care, he was equally capable of impressive insensitivity towards girls' feelings towards him. Well, perhaps it was simply that he saw them not as female suitors, but merely as his students. Tressa studied his face in profile as she caught up to him.

"Hey, Professor, can I ask you kind of a weird question?"

"What is it, Tressa?"

"Why didn't you really object? When I said I was going, I mean." Even though he seemed worried for her, his resistance was at most mild before he agreed to her coming along. Something about her fatigue lasting into the next day. Even so, when she'd burst out with her "I'm going too!" he'd not said anything at all at first.

"Hmm... That's a rather difficult question."

"Huh? Really?"

Cyrus smiled faintly as he elaborated, "Even when I was working at the Royal Academy, it was rare for me to have pupils ask such difficult questions. It's true that, as the adult in this situation, perhaps I should have been more opposed to you joining me..."

"Right."

"If I were to speak honestly, though, I think it was that I was delighted at your suggestion." Tressa's eyes widened. She hadn't expected him to say anything like that at all.

"D-delighted?"

"That's right. I think if I were to search for an appropriate word for it, that would suffice." The way Cyrus spoke was always impossibly circuitous. When she tried to square what "delighted" could possibly mean inside his head with his normal speech and conduct, she couldn't help but feel as though she were trying to solve a jigsaw puzzle with pieces missing. She thought about trying to probe him further to reclaim those pieces, but in the end decided to keep her mouth shut.
\newline

"Ah, I do believe we're here." They'd just arrived at a sandy beach, not far separated from the sea road by which they'd made camp. At their feet, lying in wait, was the gaping maw of a large cave. Tressa realized this must have been his destination. This was new to even her, who'd been born and raised in the Coastlands.

"I had no idea there was such a huge cave this close to Rippletide..."

"I chanced across it some years ago doing fieldwork in the Coastlands. It piqued my interest immediately, but my original pursuit offered me no time to investigate." Cyrus held up their lantern, shining it into the cave. It was hard to understand how such a cave could be surrounded by nothing but sandy beach, but they were nevertheless assured by the overpowering scent of the sea.

"The entrance facing the sea at such a small distance has allowed the waves to erode it in quite a curious way, don't you think? It's a most mysterious place." Cyrus' face took on a strange light as he spoke. His youthful looks already made it difficult to believe he was in his thirties, but at times like this his smile was like a little kid's. That wasn't quite it; it was as though the man was embodying curiosity and drive itself. 

"Y-yeah..." Tressa warily peeped into the entrance to the cave. She was still filled more with unease than curiosity at the moment. Then -- with an "Ah!", she stepped into the cave.

"Tressa?"

"Over here, Professor! Come look at this!" Tressa had picked up a spiral shellfish that had been stuck along the entrance wall. Amidst the darkness, its shell gleamed with a brilliant fluorescence. "It's a glassfish! I've never seen one this big before!"

"Oh my... Now that you mention it, Tressa, there certainly were a good  many shells strewn along the beach on the way here."

"All the kids in the Coastlands gather them up so they can sell 'em for a little pocket money." Glassfish shells and their shattered fragments were common sights along Coastland beaches. The beautiful transparent shells reflected light, shining red and blue. There were people in the area who made a livelihood out of trawling up and down the beaches for them, making a couple leaves out of each one. When Tressa was younger, she'd done the same. Yet although the shells were plentiful across the shore, it was much rarer to see a live glassfish, much less one like this.

"I see... The translucent shell refracts light, making the body appear as though it were glowing..." Looking intently at the glassfish perched upon Tressa's palm, Cyrus nodded eagerly.

"I can't believe we found one in a place like this... I wonder if there are any more..."

"I'd say the probability is quite high. From the look of things, I'd take it people rarely set foot in this cave at all."

"Somehow," Tressa gulped, "somehow, it's a little thrilling."

"...Isn't it?" Cyrus' lips slackened into a boy's loose grin.
\newline

Even after only walking a short distance, the passage became unexpectedly wide, opening up into a vast, complicated underground cavity. If they strained their ears, they could hear the faint echo of the waves lapping at some distant corner of the cave -- another sign of its mysterious entwining with the sea. The air was perfectly clear, with a distinct sensation in their lungs. Cyrus and Tressa continued their investigation, their footsteps echoing in the serene cavern. About ten steps in, Tressa noticed another glassfish stuck to the side of a boulder. Although she was trying not to accidentally take too many, she nevertheless gleefully tucked it away into her bag. 

"Oh, I wish I could tell my younger self about this place! I coulda made a pretty penny here." 

As for Cyrus, he was walking a couple steps away. "Tressa, rather than going straight forward, let's take this passage to the right here."

"Ah, okay!" Tressa had been single-mindedly following the trail of glassfish, snatching them up with abandon, but at Cyrus' words, she swiveled around and went to go file behind him.

"What about you, Professor? Find anything interesting?"

"Indeed, this entire place is richly fascinating. I'm glad we decided to take this little nighttime excursion."

"Hehe, me too." Tressa grinned and looked up at the ceiling. Finding so many high-quality glassfish naturally had lifted her mood considerably, but she was enjoying the cave expedition as a whole much more. She loved the sensation of being somewhere new. The scent of an unfamiliar wind blowing through this cave, a place she'd never even known was so close to Rippletide, delighted her. 

">The world is full of treasure,> huh?" She remembered those words written in her journal, words she'd read over and over, time and time again. She wasn't sure if it could be called treasure, but the experience of discovering an unexpected place so close to somewhere so familiar to her filled her heart with a certain kind of joy.

"Come to think of it, Professor, haven't you noticed how there aren't any monsters in here?" They'd only been walking a short while, but the thought tumbled from Tressa's mouth nonetheless. They weren't terribly strong, but even the Caves of Maiya to the west of Rippletide were well known to contain monsters. When Tressa had business there, she tended to only need to bring the bare minimum of equipment to fend them off. Ever since she'd set off with Cyrus and the others, they'd ventured into caves many times; without exception, they too had always met with monsters. Just as inevitably, she always managed to use her keen eye to make off with some valuable minerals to exchange for leaf later.

It was with this in mind that Tressa found the absence of monsters in this particular cave so unusual. But then Cyrus said, breezily,

"Oh, there most certainly are, Tressa. As far as I can tell, it seems we've only managed to take a detour around their usual routes thus far."

"H-huh?" Tressa whipped around to find Cyrus once again studying the ground intently. As though he felt her gaze, he looked up and gestured with his head past the edge of the path. Amidst the cave's complex, intertwining network of passageways, the one they presently walked was suspended over another below, stretching across like a bridge. She peeked over the edge at where Cyrus indicated, and--

--she felt a gasp escape her lungs. Prowling below them was a colossal monster the likes of which Tressa had never seen. It looked as though a whale had sprouted limbs and crawled out of the ocean. Though they had entered the cave not long ago, she couldn't believe she hadn't yet noticed such an enormous beast walking along with them.

"P-Professor, do you mean... you knew this whole time!?"

"Not from the start, of course not. If I'd known it was so dangerous, I never would have taken you along." He crept to Tressa's side, all the while fixing his eyes on the monster's movements. Could it be that when he was so furtively studying the ground and the walls of the cave, he was really searching for its tracks...? As she watched his profile closely, he continued, surmising her unspoken question:

"...I've learned the hard way that although studying the nature of a newfound monster is deeply fascinating, it is an indispensable skill for any scholar to be able to handle themselves when encountering with such fearsome beasts."

"A narrow escape from death, huh... I'm glad I didn't know about this place when I was little."

"Indeed. This would've been quite a dangerous place for little Tressa to go on her own." He began walking once more, this time moving as though to draw Tressa to him. "Let's go back, shall we? It's quite late, and I don't want to worry the others any more than I'm sure we already have."

"R-right." The image of the land-whale's hulking body wouldn't escape her mind. Her heart hammered like an alarm going off, and she clutched the glassfish she'd just picked up tightly in her hand. Could it be that it was her fault they were in this situation? That she'd been too excited and wandered too far into the dangerous recesses of the cave? If Cyrus were alone, wouldn't he have turned back the instant he saw these huge monsters? Tressa began to worry.

Cyrus gave her no time to stew in her thoughts, though, as he said,

"I was well aware of the danger this cave could pose only minutes after we entered. It's nothing you need worry yourself over, Tressa."

"R-really...?"

"Really." Cyrus' voice was calm and steady, as it somehow always was. No matter what the danger was, he never wavered and he never lost his wits. His unflappability had saved Tressa and the others time and time again. Yet it was precisely because he was so constantly composed that at times like these she couldn't quite tell what he was thinking. It made her a little nervous.

"Hm." Cyrus glanced over his shoulder. "It may have been somewhat imprudent of me -- irresponsible, even -- but I wanted to avoid causing you too much worry. That's why I didn't speak up earlier."

"Huh?" \emph{What's he saying all of a sudden,} Tressa thought. A faint smile played at Cyrus' lips. He laid a hand on the cave wall and looked to the ceiling.

"You know, Tressa. I personally find these conditions to be great fun."

"You mean... finding all these new things in this cave?"

Cyrus nodded. "That's right. To venture into foreign surroundings and experience all their new and unknown contents...it's a wonderful experience. But that's not all."

"Watching you walking ahead of me, likewise exploring those new surroundings and taking in everything around us...seeing the joy of discovery on your face -- now that's something I certainly couldn't experience alone." It was then that Tressa remembered what Cyrus had said shortly before they entered the cave. \emph{I was delighted} -- that was the reason he hadn't objected to taking her along. They had arrived at the mouth of the cave just then and she forgot to question him further, but those words had been nagging at her ever since.

"It's a unique delight to watch sensitive young people like yourself awaken to the joy of discovery. That's why I didn't want to worry you -- and why I would be grateful if you were able to keep on just as you have up until now." So that was it. Tressa felt a lump in her chest. Cyrus' roundabout way of talking always made him feel a little distant, but she could tell he was being truly genuine. That this was the reason he'd brought her along and ventured into this cave with her -- it was surprisingly satisfactory.

"You know, you really do live up to the 'Professor' in 'Professor Albright!'"

"I'm not quite certain how to interpret that, but I'll choose to take it as a compliment. Thank you, Tressa." Once more wearing that gentle smile, he turned back to the path ahead of them.

"Of course, my self-indulgence and the danger of this cave are two separate matters entirely. As the adult who brought you here, the proper thing to do would be for us to turn back and return to camp in one piece."

"Yes, please, Professor Albright!" Cyrus began walking once more, and Tressa followed suit.

"Say, Professor, what was that monster from before, anyway?"

"Hm. Indeed, that's an excellent question, Tressa. I must confess this is my first time seeing something quite like it firsthand. The literature shows that similar creatures exist in the Coastlands, but to my knowledge, this is the first any have been found so close to Rippletide. If I recall, the previous sightings were near the western end of the highway to Grandport." 

"Grandport, huh... I wonder if I'll ever have the chance to visit it myself..." There were too many places in the world she hadn't yet gone. Could her dream to see them all really come true? Tressa still didn't have the first clue what kind of things could be found in a place like Grandport.

They had only been walking for a short while when Cyrus stopped once more. He held out one hand to stop Tressa and put the index finger of the other to his lips.

There was a monster. Treading as lightly as she could to avoid making a sound, she crept to Cyrus' side and peeked ahead of them.

"Professor... that's..."

"A monster like that...that, too, is rare to see in these parts." At the end of the passage before them, a group of enormous crabs were clustered together. Of course, compared to the land-whale from earlier, they were positively tiny, but they were still each nearly as big as a person. Their bodies were a sickening, ominous color, and Tressa couldn't avert her eyes from their jumbo-size claws.

"The literature has only documented these around the Grandport area as well. For them to be this close to Rippletide... this cave has an unusual ecosystem indeed. I can't say I'm not fascinated, but this is certainly neither the time nor place for that."

"Uh-huh... What do we do, Professor?"

Cyrus stared intently at the end of the passage, estimating its size. It was by no means narrow, but it wasn't especially wide, either. About halfway, it split into several branches. At least one of these must have been connected to an exit, as a faint breeze could be felt.

"If we can divert the monsters and sprint for the exit, we should be able to make it out...Tressa, can you run?"

"You bet! My feet are raring to go!" The morning's exhaustion had all but disappeared -- presumably thanks to Alfyn's cold compress.

"At my signal, we run for it. Now then..."
% STOPPED AT PAGE 47